---
title: "PsiChiR: March 2020"
author: "Jen Richmond"
date: "11/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

You will be using this dataset: https://osf.io/jfdtk/

The data set is from this publication: https://cdn.ymaws.com/www.psichi.org/resource/resmgr/journal_2019/24_2_crambletalvarez.pdf

A codebook can be found here: https://osf.io/bkd5m/

You can complete and submit R script for any of the four levels, but higher levels require the completion of lower levels (in other words, if you want to turn in Level 3 script, you'll need to also do levels 1 and 2).

# load packages

You will need tidyverse, here, janitor, papaja, and jmv
```{r load packages, message=FALSE, warning=FALSE}



```

# read the data

Read in the March.csv data from the data folder using read_csv. use the here package to tell R where the data is. 

```{r read data}



```

# select the variables you need
Lets start by making teh data smaller/easier to work with. The exercise only needs you to interact with gpa, scores for male, female, poc, white, and gender of the participant. Lets start by selecting just those variables plus age and ethnicity

```{r select data}



```


#Level 1 : sort

Sort the data by GPA from low to high.

Use the names function to get a list of variables, which one has GPA in it?
```{r get variable names}



```

Use arrange to sort by gpa. Sort ascending (low to high) first, then use - to sort descending (high to low)

```{r sort data}



```

```{r}

```


#Level 2 : summarise
Produce the means and standard deviations for the following variables:

Male_score (recognition for male psychologists like Sigmund Freud; higher scores = more recognition)

Female_score (recognition for psychologist women)

POC_score (recognition for psychologists of color)

White_score (recognition for white psychologists)

Use dplyr summarise variants (_at) to get mean/sd of multiple columns. 

```{r get mean_sd}

      

    
```

```{r}


```


Get mean and sd at the same time by giving a list of functions. This creates new columns for fn1 and fn2 (option1), it would be nice if it would name them. Get that using purrr lamdas (option2) or explicitly naming them (option3) 

```{r get mean sd together}


```

More info about summarise_at/all/if variants here. 

https://dplyr.tidyverse.org/reference/summarise_all.html

# Level 3 : stats

Create a graph to compare the mean scores for recognition of women and for recognition of men.

We haven't made the data long yet. Lets do that before we plot. 

Create a df with just participant gender, gender, ethicnity, gpa, and scores for men, women, colour

```{r make data long}

```

Summarise and plot by gender of pioneer. 

```{r summarise and plot means}

```


Level 4: 
Run an independent-samples t-test comparing the mean recognition of women (Female_score) variable across male and female participants (Gender).

Make new df, with just female scores

```{r filter just female recog scores}

```

The jamovi software has a nice R package called 'jmv' associated with it with wrappers for simple stats functions. 

The independent samples t-test code looks like this

```
# template code
ttestIS(formula = DV ~ group, data = df)

# our case
ttestIS(formula = score ~ gender, data = female)

```
In this case, this will throw an error the first time because there are 3 levels of gender in this dataset. Go back to the codebook, gender has 3 levels, 1 = male, 2 = female, 3= other. Confirm this using the unique() function. 

```{r get unique values gender}

```
Need to filter out `other` to get independent samples t-test to work. 

```{r filter out other}

```

Try t-test again...

Assign output to object called results, look at ttest table for that object using results$ttest, convert it to a dataframe to make it easier to refer to parameters. 

```{r run ttest}


```



