---
title: "psichi March-May 2020"
author: ""
date: ''
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r}
library(tidyverse)
library(here)
library(janitor)
```

# read data 

```{r}
data <- read_csv(here("data", "PsichiR_pilot.csv"))
```

# March 2020

For this contest, you will be using this dataset: https://osf.io/jfdtk/

The data set is from this publication: https://cdn.ymaws.com/www.psichi.org/resource/resmgr/journal_2019/24_2_crambletalvarez.pdf

A codebook can be found here: https://osf.io/bkd5m/


## Level 1

Level 1: Sort the data by GPA from low to high.

## Level 2

Level 2: Produce the means and standard deviations for the following variables:

Male_score (recognition for male psychologists like Sigmund Freud; higher scores = more recognition)
Female_score (recognition for psychologist women)
POC_score (recognition for psychologists of color)
White_score (recognition for white psychologists)


## Level 3

Level 3: Create a graph to compare the mean scores for recognition of women and for recognition of men.

## Level 4

Level 4: Run an independent-samples t-test comparing the mean recognition of women (Female_score) variable across male and female participants (Gender).



# April 2020

## Level 1

Level 1: Remove participants with missing responses for the variable "Age."

## Level 2

Level 2: Provide frequencies of three different age groups: How many people are Less than or equal to 20? How many people between 21-40? How many people are Greater than 40?

## Level 3

Level 3: Create 4 graphs to visualize recognition of any 4 psychologists by age of participant.

## Level 4

Level 4: Run a simple linear regression analysis to determine if you can predict recognition of male psychologists from participant age.



# May 2020

## Level 1

Level 1 (Data Processing): Write code that will compute all of the eight subscale scores (e.g. "Male_score). Note that these subscales are already present in the data set -- this will give you a good comparison to see if your code works.

## Level 2

Level 2 (Descriptive Statistics): Recreate Table 2 in the publication (bottom left of page 89) -- it doesn't have to look exactly the same, but it must have the same information as the three columns - Subscale, Mean Subscale (SD), and Median Subscale.

## Level 3

Level 3 (Data Visualization): Create a visualization that compares mean scores on the following subscales: women of color, white women, white men, and men of color.


## Level 4


Level 4 (Inferential Statistics): Write code that recreates the tests for Hypothesis 1 - paired sample non parametric wilcoxan signed ranks test (page 90). https://cdn.ymaws.com/www.psichi.org/resource/resmgr/journal_2019/24_2_crambletalvarez.pdf