---
title: "psichi March-May 2020"
author: ""
date: ''
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r}
library(tidyverse)
library(here)
library(janitor)
```

# read data 

```{r}
data <- read_csv(here("data", "PsichiR_pilot.csv"))
```

# March 2020

For this contest, you will be using this dataset: https://osf.io/jfdtk/

The data set is from this publication: https://cdn.ymaws.com/www.psichi.org/resource/resmgr/journal_2019/24_2_crambletalvarez.pdf

A codebook can be found here: https://osf.io/bkd5m/


## Level 1

Level 1: Sort the data by GPA from low to high.

## Level 2

Level 2: Produce the means and standard deviations for the following variables:

Male_score (recognition for male psychologists like Sigmund Freud; higher scores = more recognition)
Female_score (recognition for psychologist women)
POC_score (recognition for psychologists of color)
White_score (recognition for white psychologists)


## Level 3

Level 3: Create a graph to compare the mean scores for recognition of women and for recognition of men.

## Level 4

Level 4: Run an independent-samples t-test comparing the mean recognition of women (Female_score) variable across male and female participants (Gender).



# April 2020

## Level 1

Level 1: Remove participants with missing responses for the variable "Age."

## Level 2

Level 2: Provide frequencies of three different age groups: How many people are Less than or equal to 20? How many people between 21-40? How many people are Greater than 40?

## Level 3

Level 3: Create 4 graphs to visualize recognition of any 4 psychologists by age of participant.

## Level 4

Level 4: Run a simple linear regression analysis to determine if you can predict recognition of male psychologists from participant age.



# May 2020

## Level 1

Level 1 (Data Processing): Write code that will compute all of the eight subscale scores (e.g. "Male_score). Note that these subscales are already present in the data set -- this will give you a good comparison to see if your code works.

## Level 2

Level 2 (Descriptive Statistics): Recreate Table 2 in the publication (bottom left of page 89) -- it doesn't have to look exactly the same, but it must have the same information as the three columns - Subscale, Mean Subscale (SD), and Median Subscale.

## Level 3

Level 3 (Data Visualization): Create a visualization that compares mean scores on the following subscales: women of color, white women, white men, and men of color.


## Level 4


Level 4 (Inferential Statistics): Write code that recreates the tests for Hypothesis 1 - paired sample non parametric wilcoxan signed ranks test (page 90). https://cdn.ymaws.com/www.psichi.org/resource/resmgr/journal_2019/24_2_crambletalvarez.pdf


# read data 

```{r}
data <- read_csv(here("data", "NICE CROWD DATA.csv"))
```


# Sept 2020 

Our September 2020 contest uses data from Psi Chi's NICE:CROWD project.


Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Remove cases that have missing values on "Countryborn"

## Level 2

Level 2: Find frequencies for the following variables: UserLanguage, Gender, and Race

## Level 3
Level 3: Create a scatterplot to visualize the relationship between vertical collectivism (COSvcollect) and horizontal collectivism (COShcollect)

## Level 4

Level 4: Calculate Pearson's R correlation coefficient between vertical collectivism and horizontal collectivism. 

# Oct 2020

Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Create a new variable "Duration in minutes" by taking the variable "Duration__in_seconds_" and dividing it by 60.

## Level 2

Level 2: Find the median for this new variable.

## Level 3

Level 3: Create a bar graph to display medians for men and women.

## Level 4

Level 4: Test whether men and women differ on this variable.



# Nov 2020

Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Recode the FACES satisfaction subscale ("FACEsatis") into three categories: Low (10 - 23), Medium (24 - 37), and High (38 - 50)

## Level 2

Level 2: Calculate the means and standard deviations for the following variables: SSBQTotal, FACEchaotic, and SDQprosocial.

## Level 3
Level 3: Create a bar graph to compare the SSBQTotal means across FACEsatis groups. Include 95% confidence interval error bars

## Level 4
Level 4: Test the hypothesis that SSBQTotal scores differ across the three FACEsatis groups.

# Dec 2020

Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Subset and filter your data so you have a dataset that excludes participants with missing values for "Race" and "Gender", and includes only these two variables plus the variable "COShcollect" (horrizontal collectivism)

## Level 2
Level 2: Calculate the means and standard deviations for COShcollect for all gender categories.

## Level 3
Level 3: Create a line graph that displays mean COShcollect scores for different race categories, with separate lines for each gender.

## Level 4

Level 4: Conduct a factorial ANOVA to compare COShcollect scores across race and gender.