---
title: "2021_12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(here)
library(foreign)
library(correlation)

```


Our OCTOBER 2021 through JANUARY 2022 contests use Hookup data from Goyette & Spencer (2021).

https://osf.io/v4yhu/ contains information about the study.

https://osf.io/9chb7/ contains an SPSS (.sav) file, that can be imported into R using the "foreign" package. Here are instructions on doing this.

```{r}
hookup <- read.spss(here("data", "Hookup.sav"), to.data.frame = TRUE)


glimpse(hookup)
```


# October 2021

Your tasks for the PsiChiR contest include:

Level 1: Remove participants who say they are in a relationship (using variable “RelStatus”, 1 = Single, 2 = in a relationship)

```{r}
unique(hookup$RelStatus)

single <- hookup %>%
  filter(RelStatus == "Single")
```


Level 2: Compute Mean and SD for the variable “Age”

```{r}

single$Age <- as.numeric(single$Age)

single %>%
  mutate(Age = as.numeric(Age)) %>%
  summarise(mean= mean(Age, na.rm = TRUE), sd = sd(Age, na.rm = TRUE))


```
```{r}
hookup %>%
  tabyl(Gender)

single %>%
  tabyl(Religious)
```


Level 3: Create a scatterplot plotting “Age” against “HCTotal”

```{r}
single %>%
  ggplot(aes(x = Age, y = HCTotal, colour = Religious)) +
  geom_point() +
  scale_y_continuous(limits = c(0,100)) 
```


Level 4: Correlate “Age” with “HCTotal” (the extent to which participants endorse hookup culture)

```{r}
single$Age <- as.numeric(single$Age)

cor.test(single$Age, single$HCTotal)

single %>%
  select(Age, HCTotal) %>%
  correlation()

single %>%
  select(Age, AttendService, HCTotal) %>%
  group_by(AttendService) %>%
  correlation()
```


```{r}
library(jmv)

corrMatrix(single, vars = vars(HCTotal, Age, IOTotal))
```




# November 2021


Your tasks for the PsiChiR contest include:

Level 1: Remove participants who say they attend religious services

```{r}

noservice <- single %>%
  filter(AttendService == "No")

```


Level 2: Determine frequencies for “Year”

```{r}
noservice %>%
  count(Year)

noservice %>%
  tabyl(Year)
```


Level 3: Create a histogram for “HCTotal”

```{r}
noservice %>%
  ggplot(aes(x = HCTotal)) +
  geom_histogram(bins = 20)
```


Level 4: Determine whether HCTotal differs across Year

```{r}
noservice %>%
  ggplot(aes(x = HCTotal)) +
  geom_histogram() +
  facet_wrap(~Year)
```


```{r}
noservice %>%
  group_by(Year) %>%
  summarise

```


```{r}


ANOVA(formula = HCTotal ~ Year, data = noservice)

```



# December


Your tasks for the PsiChiR contest include:

Level 1:

Using “Year,” put freshmen and sophomores into one group and juniors/seniors into another group

Level 2:

Determine frequencies for this new variable – how many participants are in each new group

Level 3:

Visually compare these two groups on means for HCTotal

Level 4:

Statistically compare these two groups on means for HCTotal