---
title: "PsiChi Oct 2021-Jan 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(haven)
library(naniar) # vis_miss() 
library(ggpubr) # correlations on scatter plots
library(report)

```

# read data 

```{r}

hookup <- read_sav(here("data", "Hookup Culture Final Data 2.9.21.sav"))
 
```



Our OCTOBER 2021 through JANUARY 2022 contests use Hookup data from Goyette & Spencer (2021).

https://osf.io/v4yhu/ contains information about the study.

https://osf.io/9chb7/ contains an SPSS (.sav) file, that can be imported into R using the "foreign" package. Here are instructions on doing this.



# October 2021

Your tasks for the PsiChiR contest include:

## Level 1 

Remove participants who say they are in a relationship (using variable “RelStatus”, 1 = Single, 2 = in a relationship)

```{r}


```



## Level 2

Compute Mean and SD for the variable “Age”

```{r}

```




## Level 3

Create a scatterplot plotting “Age” against “HCTotal”


```{r}



```



## Level 4

Correlate “Age” with “HCTotal” (the extent to which participants endorse hookup culture)

```{r}


```

```{r message=FALSE, warning=FALSE}


```


# November 2021


Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Remove participants who say they attend religious services

NOTE: the reason in this case we need to tell R that we want it to filter out (!=) the "1" - in quotes, is that R thinks that the AttendService variable is characters. If we converted it to numeric using as.numeric before filtering, we wouldnt need the quotes. 


```{r}




```


## Level 2
Level 2: Determine frequencies for “Year”

```{r}

```


## Level 3
Level 3: Create a histogram for “HCTotal”

```{r}

```



## Level 4

Level 4: Determine whether HCTotal differs across Year

```{r}



```



# December


Your tasks for the PsiChiR contest include:

## Level 1

Using “Year,” put freshmen and sophomores into one group and juniors/seniors into another group

```{r}


         
         
```


## Level 2

Determine frequencies for this new variable – how many participants are in each new group

```{r}



```


## Level 3

Visually compare these two groups on means for HCTotal

```{r}




```


## Level 4

Statistically compare these two groups on means for HCTotal

```{r}


```


# January 2022

## Level 1:

Sort the file by HCTotal scores, from low to high

```{r}




```


## Level 2:

Compute mean HCTotal scores for each level of “Religion”

```{r}



```


## Level 3:

Create a line graph that shows mean HCTotal scores for two variables: Religion and AttendService

```{r}





```


## Level 4:

Determine whether there’s an interaction between Religion and AttendService on the variable HCTotal


```{r}


```

