---
title: "PsiChi: Jan-May 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# load packages
```{r}
library(tidyverse)
library(here)
library(janitor)
```

# read data 

```{r}
data <- read_csv(here("data", "LeeOutton20.csv"))
```

Our January-May 2021 contest uses data from Lee & Outton (2020).

https://osf.io/24653/wiki/home/ (links to paper and .csv)


# JANUARY CHALLENGE

Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Remove participants outside of the United States.

## Level 2

Level 2: For the remaining participants, find the mean and standard deviation for "Age."

## Level 3

Level 3: Create a histogram for "Age"

## Level 4

Level 4: Test whether "Age" differed significantly across experimental conditions ("Manipulation").



# FEB CHALLENGE


Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Remove participants outside of the United States AND participants who are not identified as "white" (white participants are coded as "1" for the variable "Race").

## Level 2

Level 2: For the remaining participants, calculate the percentage of participants who fell into each income category (1 through 5).


## Level 3
Level 3: Create a graph (such as a bar graph) that displays the M and SD for "General Support for Affirmative Action" (variable = "AA") across income groups.

## Level 4

Level 4: Test whether "General Support for Affirmative Action" (variable = "AA") differs across income group.




# MARCH CHALLENGE

Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Make a general support for AA policies score by finding the average of the AA1, AA2, AA3, AA4_r, AA5, AA7, and AA8_r variables

## Level 2

Level 2: Calculate descriptives statistics for the general support for AA policies scores based on the manipulation variable.

## Level 3

Level 3: Test the difference in general support for AA policies between the different manipulation groups.

## Level 4

Level 4: Create a graph showing the relationship between general support for AA policies and the manipulation groups.




# APRIL CHALLENGE

Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Compute a mean score for Affirmative Action support for Black Americans by adding the following variables and dividing by 8: AA_Black1, AABlack2, AA_Black3, AA_Black4, AA_Black5, AA_Black6_r, AA_Black7_r, AA_Black8.

## Level 2

Level 2: Calculate the Means and Standard Deviations for this computed variable for each "Manipulation" condition.

## Level 3

Level 3: Conduct a t-test to determine if means on this new variable differ across "Manipulation" condition.

## Level 4

Level 4: Create a bar graph to display the means and standard deviations for each condition.



# MAY CHALLENGE

Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Compute a mean score for perceived status of Black Americans score by by adding the following variables and dividing by 3: Perceived_Status1, Perceived_Status2, Perceived_Status3.

## Level 2

Level 2: Calculate the Mean and Standard Deviation for this computed variable.


## Level 3
Level 3: Calculate a correlation to determine if this new variable is associated with income.

## Level 4

Level 4: Create a scatterplot to display the association between perceived status and income.

