---
title: "Feb-June2022"
output: html_document
date: '2022-05-09'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Our FEBRUARY 2022 through JUNE 2022 contests use data from [Olshan, Vitiello, & Ratliff (2021)](https://cdn.ymaws.com/www.psichi.org/resource/resmgr/journal_2021/26_3_Olshan.pdf)

You can find the data for this study [here](https://osf.io/2qu67/?view_only=dcb2a654248447e6bc2530c0f708093f).

## load packages

```{r}

```


## read in the data

```{r}

```

# CONTEST: FEBRUARY 2022

## Level 1: 
### Write script that will compute the “TotalCog” mean score from the 18 Need for Cognition variables (cog1 through cog18)


## Level 2: 
### Create a frequencies table for the TotalCog variable

## Level 3: 
### Create a scatterplot of the relation between the TotalCog and IAT scores

## Level 4: 
### Run correlation between the TotalCog and IAT scores. Calculate probability value and CIs.


# CONTEST: MARCH 2022




## Level 1: 
### Exclude participants with missing “STEMTotal” value



## Level 2: 
### Calculate descriptive statistics for the IAT variable


## Level 3: 
### Create a box and dot plot of the IAT variable


## Level 4: 
### Calculate a one-sample t-test testing whether the sample's mean IAT score is different from zero



# CONTEST: April 2022


## Level 1: 
### Transform age variable into the following groups: 18 to 22; 23 to 30; 31 to 40; 41 to 50; over 50

## Level 2: 
### Calculate descriptive statistics for the IAT variable separately for each group of the categorical age group you just created


## Level 3: 
### Create a bar graph w/ error bars displaying the IAT scores based on the categorical age variable
## Level 4: Calculate a one-way ANOVA testing the difference in IAT scores based on the age groups

# CONTEST: MAY 2022

## Level 1: 
### Filter out the participants who are NOT currently in STEM (select Demo2 = 1)

## Level 2: 
### Calculate descriptive statistics for the IAT and STEMtotal variables

## Level 3: 
### Create a scatterplot of the relation between the IAT and STEMtotal variables

## Level 4: 
### Run correlation between the IAT and STEMtotal scores. Calculate probability value and CIs.

