---
title: "PsiChi Feb-June2022"
output: html_document
date: '2022-05-09'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Our FEBRUARY 2022 through JUNE 2022 contests use data from [Olshan, Vitiello, & Ratliff (2021)](https://cdn.ymaws.com/www.psichi.org/resource/resmgr/journal_2021/26_3_Olshan.pdf)

You can find the data for this study [here](https://osf.io/2qu67/?view_only=dcb2a654248447e6bc2530c0f708093f).

## load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(haven)
library(here)
library(janitor)
library(gt)
library(ggpubr)
library(naniar)
library(ggeasy)
library(report)
```


## read in the data

```{r}

data <- read_sav(here("data", "data_women_OSF_1.25.sav")) %>%
  clean_names()

```




#  FEBRUARY 2022

## Level 1: 
 Write script that will compute the “TotalCog” mean score from the 18 Need for Cognition variables (cog1 through cog18)
 
```{r}


```
 


## Level 2: 
 Create a frequencies table for the TotalCog variable
 
```{r}

```
 

## Level 3: 
 Create a scatterplot of the relation between the cogmean and **IAT scores**
 
```{r my-figure, fig.cap = "Figure 1: The relation between IAT scores and need for cognition scores."}


```
 

## Level 4: 
 Run correlation between the TotalCog and IAT scores. Calculate probability value and CIs.
 
```{r}

```



#  MARCH 2022


## Level 1: 
 Exclude participants with missing “STEMTotal” value
 
```{r}


```
 



## Level 2: 
 Calculate descriptive statistics for the IAT variable
 
 - mean, median
 - max, min
  - stddev, stderr
 
 
kableExtra package useful for table formatting, particularly easy to change digits to however many places you want (avoid need to add round() to every line of your summarise). 
 
 
```{r}




```
 


## Level 3:
 Create a box and dot plot of the IAT variable
 
 
```{r}


  
```


## Level 4: 
 Calculate a one-sample t-test testing whether the sample's mean IAT score is different from zero
 
```{r}



```


#  April 2022


## Level 1: 
 Transform age variable into the following groups: 18 to 22; 23 to 30; 31 to 40; 41 to 50; over 50
 
```{r}



```
 

## Level 2: 
 Calculate descriptive statistics for the IAT variable separately for each group of the categorical age group you just created
 
```{r}

```
 
 
## Level 3: 
 Create a bar graph w/ error bars displaying the IAT scores based on the categorical age variable
 
 https://jennyrichmond.netlify.app/blog/i-dont-have-to-google-series/2023-04-25-error-bars-on-plots/
 
```{r}

 

```
 

 
## Level 4: 

Calculate a one-way ANOVA testing the difference in IAT scores based on the age groups

```{r}


```


#  MAY 2022

## Level 1: 
 Filter out the participants who are NOT currently in STEM (select Demo2 = 1)
 


## Level 2: 
 Calculate descriptive statistics for the IAT and STEMtotal variables

## Level 3: 
 Create a scatterplot of the relation between the IAT and STEMtotal variables

## Level 4: 
 Run correlation between the IAT and STEMtotal scores. Calculate probability value and CIs.


## read in the data


```{r message=FALSE, warning=FALSE}

data_nov <- read_csv(here("data", "nice_data", "2022_Nov_NICE.csv")) %>%
  clean_names()

```


```{r}




```



#  Nov 2022

## Level 1: 

Write script that will select participants who are 18+ years old



```{r}


```
 


## Level 2: 

Create a variable called “SDQprosocial” that reflects prosocial behavior exhibited by participants. This is probably asking us to calculate mean scores across the 5 prosocial variable. 

SDQ = Strengths and Difficulties Questionnaire
1) emotional symptoms (5 items)
2) conduct problems (5 items)	
3) hyperactivity/inattention (5 items)	
4) peer relationship problems (5 items)	
5) prosocial behaviour (5 items)

Prosocial: 1consid, 4shares, 9pcaring, 17kind, 20helpout)






## Level 3: 

Create a bar graph to display mean scores on the SDQ variable for men and women.





## Level 4: 

Test whether men and women differ on this variable.




#  Dec 2022

## read in the data

Here I am reading teh dec data in using read-csv and here. Add clean_names to make the variables name all lower case and _ in the gaps. 

```{r message=FALSE, warning=FALSE}

data_dec <- read_csv(here("data", "nice_data", "2022_Dec_NICE.csv")) %>%
  clean_names()

```


## Level 1: 

Write script that will filter out participants who are older than 19



## Level 2: 

Create a variable called ‘FACEenmesh’ that measures participants’ levels of enmeshment with their families. To create this variable, you will add together the following items from the FACES scale: FACES4, FACES10, FACES16, FACES22, FACES28, FACES34, FACES40

Find the mean and standard deviation for enmeshment exhibited by participants as measured by the FACES



## Level 3: 
Create a bar graph to display mean scores on the enmeshment variable for men and women.

1= male
2= female

 

## Level 4: 

Test whether men and women differ on this variable.

