---
title: "PsiChi Feb-June2022"
output: html_document
date: '2022-05-09'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Our FEBRUARY 2022 through JUNE 2022 contests use data from [Olshan, Vitiello, & Ratliff (2021)](https://cdn.ymaws.com/www.psichi.org/resource/resmgr/journal_2021/26_3_Olshan.pdf)

You can find the data for this study [here](https://osf.io/2qu67/?view_only=dcb2a654248447e6bc2530c0f708093f).

## load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(haven)
library(here)
library(janitor)
library(gt)
library(ggpubr)
library(naniar)
library(ggeasy)
library(report)
```


## read in the data

```{r}

data <- read_sav(here("data", "data_women_OSF_1.25.sav")) %>%
  clean_names()

```




#  FEBRUARY 2022

## Level 1: 
 Write script that will compute the “TotalCog” mean score from the 18 Need for Cognition variables (cog1 through cog18)
 
```{r}


```
 


## Level 2: 
 Create a frequencies table for the TotalCog variable
 
```{r}

```
 

## Level 3: 
 Create a scatterplot of the relation between the cogmean and **IAT scores**
 
```{r my-figure, fig.cap = "Figure 1: The relation between IAT scores and need for cognition scores."}


```
 

## Level 4: 
 Run correlation between the TotalCog and IAT scores. Calculate probability value and CIs.
 
```{r}

```



#  MARCH 2022


## Level 1: 
 Exclude participants with missing “STEMTotal” value
 
```{r}


```
 



## Level 2: 
 Calculate descriptive statistics for the IAT variable
 
 - mean, median
 - max, min
  - stddev, stderr
 
 
kableExtra package useful for table formatting, particularly easy to change digits to however many places you want (avoid need to add round() to every line of your summarise). 
 
 
```{r}




```
 


## Level 3:
 Create a box and dot plot of the IAT variable
 
 
```{r}


  
```


## Level 4: 
 Calculate a one-sample t-test testing whether the sample's mean IAT score is different from zero
 
```{r}



```


#  April 2022


## Level 1: 
 Transform age variable into the following groups: 18 to 22; 23 to 30; 31 to 40; 41 to 50; over 50
 
```{r}



```
 

## Level 2: 
 Calculate descriptive statistics for the IAT variable separately for each group of the categorical age group you just created
 
```{r}

```
 
 
## Level 3: 
 Create a bar graph w/ error bars displaying the IAT scores based on the categorical age variable
 
 https://jennyrichmond.netlify.app/blog/i-dont-have-to-google-series/2023-04-25-error-bars-on-plots/
 
```{r}

 

```
 

 
## Level 4: 

Calculate a one-way ANOVA testing the difference in IAT scores based on the age groups

```{r}


```


#  MAY 2022

## Level 1: 
 Filter out the participants who are NOT currently in STEM (select Demo2 = 1)
 


## Level 2: 
 Calculate descriptive statistics for the IAT and STEMtotal variables

## Level 3: 
 Create a scatterplot of the relation between the IAT and STEMtotal variables

## Level 4: 
 Run correlation between the IAT and STEMtotal scores. Calculate probability value and CIs.

