---
title: "Psichi Nov2022-Nov2023"
output: html_document
date: "2023-11-14"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Level 1 data processing
Level 2 descriptive statistics
Level 3 data visualisation
Level 4 inferential statistics

Data for this contest is from Psi Chi's Network for International Collaborative Exchange (NICE). 

Specifically, this data is from the first project ever run by NICE - Understanding Family Dynamics in a Cross-Cultural Sample. 


You can find the data for this study [here](https://osf.io/pwe94).

## load packages


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(report)
library(papaja)
library(RColorBrewer)
library(ggeasy)
```




#  Jan 2023

## read in the data

```{r}

data_jan <- read_csv(here("data", "nice_data", "2023_Jan_NICE.csv")) %>%
  clean_names()

```


## Level 1: 

Write script that will filter out participants who do not have any siblings




## Level 2: 

Create a variable called ‘FACEcomm’ that measures participants’ levels of communication with their families. 

To create this variable, you will add together the following items from the FACES scale: FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52


Find the mean and standard deviation for communication exhibited by participants as measured by the FACES.



## Level 3: 

 Create a bar graph to display mean scores on the communication variable for men and women.
 
 

## Level 4: 

Test whether communication differs based on the number of siblings someone has.

Make this problem easier by filtering only siblings 1, 2 or 3. 


#  Feb 2023

> filter out NAs, compute new variable with sum, summarise mean, sd, median, quartiles, plot bar graph, do t.test
- 

## read in the data

```{r}

data_feb <- read_csv(here("data", "nice_data", "2023_Feb_NICE.csv")) %>%
  clean_names()

```

## Level 1: 


Write script that will filter out participants who are missing a value for the Age variable
 

```{r}


```
 


## Level 2: 
Create a variable called ‘FACErigid’ that measures rigidity among families. To create this variable, you will add together the following items from the FACES scale: FACES5 + FACES11 + FACES17 + FACES23 + FACES29 + FACES35 + FACES41
 
Find the mean, standard deviation, median, and lower and upper quartiles for rigidity exhibited by participants as measured by the FACES
 
 
```{r}

```
 

## Level 3: 
Create a bar graph to display mean scores on the rigidity variable for men and women.
 
 
```{r}


```

## Level 4: 

Test if levels of rigidity differ by gender of participant. 

```{r}



```
 
#  March 2023 

> filter by 2 variables, compute new variable with sum, summarise mean, sd, median, range, plot bar graph, do t.test

## read in the data

```{r}

data_mar <- read_csv(here("data", "nice_data", "2023_March_NICE.csv")) %>%
  clean_names()

```
## Level 1: 


Write script that will filter out participants who are missing a value AND who are older than 18for the Age variable
 

```{r}


```
 


## Level 2: 
Create a variable called ‘PsyContF’ that measures Psychological Control exhibited by the respondent’s Father. To create this variable, you will add together the following items from the DYADS scale: DyadF1+ DyadF2+ DyadF3+ DyadF4+ DyadF5+ DyadF6+ DyadF7
 
Find the mean, standard deviation, median, and range for psychological control exhibited by respondent’s fathers as measured by the DYADS
 

 
```{r}

```
 

## Level 3: 

 Create a bar graph to display mean scores of the PsyContF variable reported by men and women.


```{r}


```

## Level 4: 
Test if levels of reported PsyContF differ by gender of participant.
```{r}



```

#  April 2023 

> filter 2 variables, compute 2 new variables with sum, summarise mean, sd, median, quartiles, plot scatter, do correlation


## read in the data

```{r}

data_apr <- read_csv(here("data", "nice_data", "2023_Apr_NICE.csv")) %>%
  clean_names()

```
## Level 1: 


Write script that will filter out participants who are missing a value for the Age variable
Write a script that will filter out participants who identify as men
 
Note: you can combine filter with AND & or you can specify a combination of filters with a OR operator |


```{r}


```
 


## Level 2: 

 Create a variable called ‘SDQhyper’ that measures x exhibited by the participant. To create this variable, you will add together the following items from the SDQ scale: SDQ2 + SDQ10 + SDQ15 + SDQ21 + SDQ25
 
Create a variable called ‘SUtotal’ that measures all substance use exhibited by the participant. To create this variable, you will add together the following items from the YRBS scale: YRBS1 + YRBS2 + YRBS3 + YRBS4 + YRBS5 + YRBS6 + YRBS7 + YRBS8 + YRBS9 + YRBS10 + YRBS11 + YRBS12 + YRBS13 + YRBS14 + YRBS15 + YRBS16 + YRBS17
 
Find the mean, standard deviation, median, and range for SDQhyper
 



## Level 3: 

Create a graph to display levels of hyperactivity as a function of age



## Level 4: 
Test if there is an association between substance use and reported hyperactivity



#  May 2023 

## read in the data

```{r}

data_may <- read_csv(here("data", "nice_data", "2023_May_NICE.csv")) %>%
  clean_names()

```
## Level 1: 

Write a script that will filter out participants who are missing a value for the ‘Siblings’ variable.


```{r}


```
 


## Level 2: 
Create a variable called ‘FACEdisen’ that measure family disengagement by adding the following items together: FACES3, FACES9, FACES15, FACES21, FACES27, FACES33, FACES39

Create a variable called ‘FACEenmesh’ that measures family enmeshment by adding the following items:  FACES4, FACES10, FACES16, FACES22, FACES28, FACES34, FACES40

Create a variable called ‘FACEcomm’ that measures family communication by adding together the following items: FACES43, FACES44, FACES45, FACES46, FACES47, FACES48, FACES49, FACES50, FACES51, FACES52

Find the mean, standard deviation, median, and range for ‘FACEdisen’, ‘FACEenmesh’, and ‘FACEcomm’. Report the average number of siblings reported by participants and indicate the range. 
 
```{r}

```
 

## Level 3: 

Create a histogram for “FACEcomm”


```{r}


```

## Level 4: 

Test if there is an association between the number of siblings reported by participants and family disengagement, enmeshment, and communication. 

```{r}



```


#  June 2023

> filter out NAs, recode variable, compute new variable with sum, summarise mean, sd, median, quartiles, plot bar graph, do correlation


## read in the data

```{r}

data_jun <- read_csv(here("data", "nice_data", "2023_Jun_NICE.csv")) %>%
  clean_names()

```
## Level 1: 



• Write script that will filter out participants who are missing a value for the Age variable
• Write a script that will recode text entries in the SexOrient Column to Numbers
o Heterosexual should be 1 
o Non-heterosexual should be 2
 

```{r}


```
 

## Level 2: 

 • Create a variable called ‘FACEcomm’ that measures family communication. To create this variable, you will add together the following items from the FACES scale: FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52
 
• Create a variable called ‘FACEdisen’ that measures family disengagement. To create this variable, you will add together the following items from the FACES scale: FACES3 + FACES9 + FACES15 + FACES21 + FACES27 + FACES33 + FACES39 
 
• Create a variable called ‘SUtotal’ that measures all substance use exhibited by the participant. To create this variable, you will add together the following items from the YRBS scale: YRBS1 + YRBS2 + YRBS3 + YRBS4 + YRBS5 + YRBS6 + YRBS7 + YRBS8 + YRBS9 + YRBS10 + YRBS11 + YRBS12 + YRBS13 + YRBS14 + YRBS15 + YRBS16 + YRBS17
 
• Find the mean, standard deviation, median, and range for FACEcomm, FACEdisen, and SUtotal
 
```{r}

```
 

## Level 3: 
• Create a graph that will show levels of family communication reported by men and women
 
```{r}


```

## Level 4: 
 

• Test if there is an association between substance use and family communication and disengagement
```{r}



```


#  July 2023**

> filter by 1 variable, compute new variable with sum, summarise mean, recode w case_when, make a table of counts, anova?

## read in the data

```{r}

data_jul <- read_csv(here("data", "nice_data", "2023_Jul_NICE.csv")) %>%
  clean_names()

```
## Level 1: 

• Write a script that will filter out participants who don’t have any siblings



```{r}


```
 


## Level 2: 

 • Create a variable called SUmarij by adding YRBS8 + YRBS14
• Find the average number of times participants have used marijuana.
• Transform SUmarij into a binary variable where 0 = never used marijuana, and 1 = has used marijuana 


```{r}

```
 

## Level 3: 

 • Use cross-tabs to make a table that shows the counts of marijuana use (never used/has used) by gender
 

```{r}


```

## Level 4: 
• Test if there is an association between marijuana use and number of siblings someone has

```{r}



```


#  August 2023

> filter out NAs, compute new variables WITH reverse scoring with sum, summarise mean, sd, median, quartiles, plot bar graph, do correlation

## read in the data

```{r}

data_aug <- read_csv(here("data", "nice_data", "2023_Aug_NICE.csv")) %>%
  clean_names()

```
## Level 1: 


• Write a script that will filter out participants who are missing values for the age variable


```{r}


```
 


## Level 2: 

• Create a variable called FACEcomm (Family Communication) by adding together the following items FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52
o Note the average, standard deviation, and median values for the FACEcommvariable.

• Create a variable called SSBQtotal (Total Safe Sex Behavior) through two steps
o 1. Reverse Score SBQ2 INTO SBQ2R, SBQ7 INTO SBQ7R, SBQ8 INTO SBQ8R, SBQ14 INTO SBQ14R, SBQ16 INTO SBQ16R, SBQ17 INTO SBQ17R, SBQ22 INTO SBQ22R, SBQ24 INTO SBQ24R, SBQ25 INTO SBQ25R
▪ 1 = Always 2 = Most of the time 3 = Sometimes 4 = Never

o 2. Add the following items together: SBQ1 + SBQ2R + SBQ3 + SBQ4 + SBQ5 + SBQ6 + SBQ7R + SBQ8R + SBQ9 + SBQ10 + SBQ11 + SBQ12 + SBQ13 + SBQ14R + SBQ15 + SBQ16R + SBQ17R + SBQ18 + SBQ19 + SBQ20 + SBQ21 + SBQ22R + SBQ23 + SBQ24R + SBQ25R
o Note the average, standard deviation, and median values for the SSBQtotalvariable
 
```{r}

```
 

## Level 3: 

 
• Create a bar graph that shows the mean levels of FACEcomm and SSBQtotal
```{r}


```



## Level 4: 
• Test if there is an association between total safe sex behavior (SSBQtotal) and family communication (FACEcomm).
```{r}



```


#  Sept2023

> filter out NAs, compute new variables with sum, summarise mean, sd, median, quartiles, plot bar graph, do correlation and t.test

## read in the data

```{r}

data_sep <- read_csv(here("data", "nice_data", "2023_Sept_NICE.csv")) %>%
  clean_names()

```
## Level 1: 

• Write a script that will filter out participants who are missing values for the ‘Age’ variable
• Write a script that will filter out participants who are missing values for the ‘Stateborn’ variable



```{r}


```
 


## Level 2: 

 • Create a variable called ‘CFPSCompas’ by summing together the following variables: FPS7, FPS8, FPS9, FPS10
o CFPSCompas is a variable that measures Compassionate Reverence 
• Create a variable called ‘FACEsatis’ by summing together the following variables: FACES53, FACES54, FACES55, FACES56, FACES57, FACES58, FACES59, FACES60, FACES61, FACES62
o FACEsatis is a variable that measures Family Satisfaction


```{r}

```
 

## Level 3: 
• Create a graph that shows the mean levels of Family Satisfaction by gender 

 
```{r}


```

## Level 4: 
• Test if there is an association between Compassionate Reverence and Family Satisfaction. Note any key statistics.
• Test if there are any gender differences in mean levels of Family Satisfaction. Note any key statistics.
```{r}



```




#  Nov 2023

> filter out NAs, compute new variable with sum, summarise mean, sd, median, quartiles, plot bar graph, create correlation matrix

## read in the data

```{r}

data_nov <- read_csv(here("data", "nice_data", "2023_Nov_NICE.csv")) %>%
  clean_names()

```
## Level 1: 


·   	Write a script that will filter out participants who are missing values for the ‘Hoursmom’ and ‘Hoursdad’ variables
·   	Create a variable called ‘PsyContM’ by summing together the following variables: DyadM1+ DyadM2+ DyadM3+ DyadM4+ DyadM5+ DyadM6+ DyadM7
·   	Create a variable called ‘PsyContF’ by summing together the following variables:  DyadF1+ DyadF2+ DyadF3+ DyadF4+ DyadF5+ DyadF6+ DyadF7



```{r}


```
 


## Level 2: 

 ·   	Calculate the mean, standard deviation, median, and range for PsyContM and PsyContF
```{r}

```
 

## Level 3: 

Create a correlation matrix for Hoursmom, Hoursdad, PsyContM and PsyContM
 
```{r}


```

## Level 4: 
·   	Is there a significant correlation between PsyConF and Hoursdad? Note the R and P values.
```{r}



```


#  Dec 2023 **

> get descriptives, correlation, recoding, anova


## read in the data

```{r}

data_dec <- read_csv(here("data",  "Flight Data December 2023 Contest.csv")) %>%
  clean_names()

```

## Level 1: 

Provide descriptive statistics for the actual_flown_miles variable. Indicate the minimum number of miles flow, the maximum number of miles flow, the average number of miles flown, and the median number of miles flown.
```{r}


```
 


## Level 2: 

Describe the relationship between satisfaction (satisfaction_score) and delay time (arrival_delay_minutes). Note that for satisfaction_score a value of 1 is the lowest (dissatisfied) and 5 is the highest (satisfied). 

Note that negative values in the arrival delay minutes mean the flight was early, while positive values indicate the flight was late. 
```{r}

```
 

## Level 3: 

Does satisfaction level (satisfaction_score) vary by the cabin (cabin_code) that they’re in? 
 
```{r}


```


## Level 4: 

Describe the relationship between loyalty program membership (loyalty_program_level) and satisfaction (satisfaction_score). Hint: you’ll have to do some recoding for folks who don’t belong to a program

```{r}



```


