---
title: "psichi challenge template"
output: html_document
date: "2024-04-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Level 1 data processing
Level 2 descriptive statistics
Level 3 data visualisation
Level 4 inferential statistics

Data for this month’s contest uses IMBD’s Horror Movie Dataset available through Kaggle.com 


You can find the data for this study [here](https://www.kaggle.com/datasets/PromptCloudHQ/imdb-horror-movie-dataset).

## load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)

```


## read in the data

```{r}



```



#  Oct 2023

## Level 1: 

• Write a script that will filter out movies that are missing a value in the ‘Budget’ column. 

• Write a script that will filter out movies that are missing a value in the ‘RunTime’ column. 


```{r}


```
 


## Level 2: 

• Write a script that will provide the average, standard deviation, median, and range of the ‘RunTime’ variable. Note the values you got.  

• Write a script that will provide the average, standard deviation, median, and range of the ‘Budget’ variable. Note the values you got.  

• Write a script that will provide the average, standard deviation, median, and range of the ‘Review’ variable. Note the values you got from running the code.  

```{r}

```
 

## Level 3: 

• Create a graph that shows the ‘Budget’ for the movies in the dataset over time.  

 
```{r}


```

## Level 4: 

Test if there are any associations between the following variables: ‘Review’, ‘Budget’, and ‘RunTime’. Note the key statistics you got from running the code.

```{r}



```

