---
title: "2023_Dec_flight data"
output: html_document
date: "2024-04-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#  Dec 2023
## read in the data

```{r}

data_dec <- read_csv(here("data",  "Flight Data December 2023 Contest.csv")) %>%
  clean_names()

```
## Level 1: 

Provide descriptive statistics for the actual_flown_miles variable. Indicate the minimum number of miles flow, the maximum number of miles flow, the average number of miles flown, and the median number of miles flown.
```{r}


```
 


## Level 2: 

Describe the relationship between satisfaction (satisfaction_score) and delay time (arrival_delay_minutes). Note that for satisfaction_score a value of 1 is the lowest (dissatisfied) and 5 is the highest (satisfied). 

Note that negative values in the arrival delay minutes mean the flight was early, while positive values indicate the flight was late. 
```{r}

```
 

## Level 3: 

Does satisfaction level (satisfaction_score) vary by the cabin (cabin_code) that they’re in? 
 
```{r}


```


## Level 4: 

Describe the relationship between loyalty program membership (loyalty_program_level) and satisfaction (satisfaction_score). Hint: you’ll have to do some recoding for folks who don’t belongto a program
```{r}



```
