---
title: "psichi challenge template"
output: html_document
date: "2024-04-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Level 1 data processing
Level 2 descriptive statistics
Level 3 data visualisation
Level 4 inferential statistics

Data for this contest is from ...

You can find the data for this study [here](...).


To facilitate analyses, the ‘Runtime’ variable will need to be fixed so that ‘min’ is removed, and the column only contains numerical values.  

To facilitate analyses, the ‘Genre’ variable will need to be edited so that each genre separated by a comma is listed in its own respective column. 

## load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)

```


## read in the data

```{r}

imdb_top_1000 <- read_csv(here("data", "imdb_top_1000.csv"))

```



#  Feb 2024

## Level 1: 


To facilitate analyses, the ‘Runtime’ variable will need to be fixed so that ‘min’ is removed, and the column only contains numerical values.  

To facilitate analyses, the ‘Genre’ variable will need to be edited so that each genre separated by a comma is listed in its own respective column. 


```{r}


```
 


## Level 2: 

Provide the mean, standard deviation, median, and range of values for ‘IMDB_Rating’ 

Provide the mean, standard deviation, median, and range of values for ‘Gross’ 

```{r}

```
 

## Level 3: 

Provide the mean values for IMDB rating by Released Year

What is the mean ‘IMDB_rating’ of Romance movies?  

 
```{r}


```

## Level 4: 

Create a plot that shows the average ‘IMDB_rating’ for Romance movies over time. 

Find the star who was lead in the most romance movies 

```{r}



```


#  March 2024

This month’s data comes from Kaggle.com, we’ll be looking at the 50 most popular songs on Spotify. 


## read in the data

```{r}
top_50_2023 <- read_csv(here("data", "top_50_2023.csv"))


```


## Level 1: 

Let’s get familiar with our data. Create a table that shows how many times each genre is represented in the Top 50 most popular songs on Spotify. What is the most popular genre? 

Which artist, if any, has the greatest number of Top 50 most popular songs on Spotify? 


```{r}


```


## Level 2: 

Provide the mean, standard deviation, median, and range of values for ‘danceability’ 

Provide the mean, standard deviation, median, and range of values for ‘valence’ 

Provide the mean, standard deviation, median, and range of values for ‘energy’ 
```{r}

```
 

## Level 3: 

Does the ‘tempo’ variable meet the assumption of normality?  

Produce a visual that will show if the ‘loudness’ variable contains any outliers.  

Is there a significant difference in the ratings of ‘danceability’ for explicit songs, compared to songs that are not explicit? Note all key statistics. 
 
```{r}


```

## Level 4: 

Create a regression model to figure out which of the following is the strongest predictor of popularity: danceability, valence, energy, loudness, acousticness. Instrumentalness, liveness, speechiness, or tempo. Please note all key statistics for each variable. 

 

```{r}



```

