---
title: "2025_jan-april"
output: html_document
date: "2025-03-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Level 1 data processing
Level 2 descriptive statistics
Level 3 data visualisation
Level 4 inferential statistics

Data for this contest is from ...

You can find the data for this study [here](...).

## load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)

```


## read in the data

```{r}



```

#  Jan 2025

## Level 1: 


January is National Cheese Lover’s Day

Level 1. Remove any rows where ‘company,’ ‘product_name,’ and/or ‘rating’ are blank.
```{r}


```
 

## Level 2: 
Level 2. Make one table that shows the counts of each category within ‘rating,’ and then make a second table showing counts for each ‘country.’ 

```{r}

```
 

## Level 3: 

Level 3. First, make a table showing how many of each medal type (rating) each cheese (Category_Corrected). Which cheese has the most “Super Golds?” Next, modify the table and indicate which country produced the most “Super Gold” cheeses. 
```{r}


```

## Level 4: 
Level 4. Generate a map that shows which countries have won super gold medals.
 

```{r}



```



#  Feb 2025 lee Outten

## Level 1: 

Level 1: Remove participants outside of the United States AND participants who are not identified as "white" (white participants are coded as "1" for the variable "Race").





```{r}


```
 

## Level 2: 

Level 2: For the remaining participants, calculate the percentage of participants who fell into each income category (1 through 5).


```{r}

```
 

## Level 3: 


 Level 3: Create a graph (such as a bar graph) that displays the M and SD for "General Support for Affirmative Action" (variable = "AA") across income groups.


```{r}


```

## Level 4: 

Level 4: Test whether "General Support for Affirmative Action" (variable = "AA") differs across income group.




#  Mar 2025

## Level 1: 


Level 1: Sort the data by GPA from low to high.

```{r}


```
 

## Level 2: 

Level 2: Produce the means and standard deviations for the following variables:

GPA

Male_score (recognition for male psychologists like Sigmund Freud; higher scores = more recognition)

Female_score (recognition for psychologist women)

POC_score (recognition for psychologists of color)

White_score (recognition for white psychologists)

```{r}

```
 

## Level 3: 


Level 3: Create a graph to compare the mean scores for recognition of women and for recognition of men.


 
```{r}


```

## Level 4: 

Level 4: Run an independent-samples t-test comparing the mean recognition of women (Female_score) variable across male and female participants (Gender).

Level 4 Bonus: Run an independent-samples t-test comparing the mean recognition of women (Female_score) variable between people who have completed a history of psychology course and people who have not taken a history of psychology course (Taken_history).
```{r}



```



#  Month Year

## Level 1: 



```{r}


```
 

## Level 2: 


```{r}

```
 

## Level 3: 


 
```{r}


```

## Level 4: 


```{r}



```







```{r}



```
