---
title: "March_2020_exercises"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Apply your knowledge

The challenges below are designed to give you an opportunity to apply what you have learned to future explore the March challenge dataset. You should expect to use a combination of arrange, select, filter, group_by, summarise, plot, and t-tests. 


#### 1. Does the ethicnity of participant impact their recognition of white vs. poc scientists?

- Create a new dataframe from the march_long data that includes only performance on white and poc trials. - Use unique() to work out how many ethicnity categories are represented in the participants. 
- Use group_by and summarise to calculate the mean performance for white and poc trials, separately for participants of each ethnic category. 
- Plot mean performance for white and poc trials separate for participants in each ethic category 

**hint:  + facet_wrap(~ ethinicity) might be useful**

### 2. Is performance correlated with gpa?

- add an pp_ID column to march_small using this code

```{r}
march_small <- march_small %>% mutate(id = row_number())
```

- then use the pivot_longer function to create the march_long dataframe again
- create a new datafram from you new march_long dataframe that averages performance across condition

**hint: using group_by(id) %>% summarise(mean_score = mean(score)) should give an average score for each id**

- plot the relation between gpa and average score using geom_point() 

https://ggplot2.tidyverse.org/reference/geom_point.html


### 3. are there gender differences in recognition of white, poc, male, and female scientists?

In the exercise, we looked particularly at whether male and female participants differed in their recognition of female scientist. Work out how to plot gender differences across all 4 conditions **hint facet_wrap() will be useful for this one too**


