---
title: "april2020_template code"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# April 2020 PsiChiR challenge

The new challenge is up!

Contest submissions: submit here.

For this contest, you will be using this dataset: https://osf.io/jfdtk/

The data set is from this publication: https://cdn.ymaws.com/www.psichi.org/resource/resmgr/journal_2019/24_2_crambletalvarez.pdf

A codebook can be found here: https://osf.io/bkd5m/

You can complete and submit R script for any of the four levels, but higher levels require the completion of lower levels (in other words, if you want to turn in Level 3 script, you'll need to also do levels 1 and 2).

For tips on getting started with R, start here: http://bit.ly/psichirtutorial


# Set up

# Load packages

here are the packages you will need. Use install.package() if you don't already have these ones installed. 

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(naniar)
library(broom)
library(kableExtra)
```


# Read in the data

The dataset is the same as from the March challenge. So practice reading it in again using read_csv, here, and clean names. 

Then go to the code book and choose your 4 favourite psychologists. Mine favourites are developmental psychologists 

- F2 Mary Ainsworth
- F9 Eleanor Maccoby 
- M25 Jean Piaget 
- M32 Albert Bandura. 

Use select to create df with age and the recognition values for your favourite 4. 

```{r}

```


# Level 1: Remove participants with missing responses for the variable "Age."

The naniar package helps you visualise and deal with missing data. Use install.packages() if you don't already have it. 

Use vis_miss() to see how much of a problem missing avalues in the Age variable are

```{r}


```
To remove participants who have missing age values, use filter and is not equal to (!=) "NA", to filter out the NA values
```{r}



```


# Level 2: Provide frequencies of three different age groups: How many people are Less than or equal to 20? How many people between 21-40? How many people are Greater than 40?

Use mutate and if_else to make a new variable that creates age groups

https://dplyr.tidyverse.org/reference/if_else.html


```{r}


                
```

Use group_by, summarise and n() to count how many participants fall into each of the 3 age groups
```{r}



```


# Level 3: Create 4 graphs to visualize recognition of any 4 psychologists by age of participant.

Use pivot_longer to make a single column with the psychologist in it. 

```{r}

```

Use recode to replace values in that column with names
```{r}

```

Use group_by and summarise to calculate mean scores by agegroup and psych_name and then 

```{r}


```


Plot using facet_wrap. 
```{r}

```

Are your age groups out of order? Use fct_relevel to make your columns be ordered young, middle, old, then plot again. 
```{r}

  
```


# Level 4: Run a simple linear regression analysis to determine if you can predict recognition of male psychologists from participant age.

Go back to the df that you read in and create a new one that includes only age and male_score, get rid of NAs in age 

```{r}

```

Plot the relation between age and male_score as scatter plot (add geom_point and geom_smooth to get an idea of whether there is a linear relation)
```{r}

```

Use lm funciton to predict male score from age
```{r}



```

Use print() to get coefficients
```{r}

```

Use summary() to get all model information
```{r}


```

Use the broom package to tidy this ugly output into a df using the tidy() function and then kable() to make a nice table. 

```{r}

```


