---
title: "psichi challenge template"
output: html_document
date: "2024-04-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Level 1 data processing
Level 2 descriptive statistics
Level 3 data visualisation
Level 4 inferential statistics

Data for this contest is from ...

You can find the data for this study [here](...).

## load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)

```


## read in the data

```{r}



```



#  Month Year

## Level 1: 



```{r}


```
 

## Level 2: 


```{r}

```
 

## Level 3: 


 
```{r}


```

## Level 4: 


```{r}



```



#  Month Year

## Level 1: 



```{r}


```
 

## Level 2: 


```{r}

```
 

## Level 3: 


 
```{r}


```

## Level 4: 


```{r}



```



#  Month Year

## Level 1: 



```{r}


```
 

## Level 2: 


```{r}

```
 

## Level 3: 


 
```{r}


```

## Level 4: 


```{r}



```



#  Month Year

## Level 1: 



```{r}


```
 

## Level 2: 


```{r}

```
 

## Level 3: 


 
```{r}


```

## Level 4: 


```{r}



```



#  Month Year

## Level 1: 



```{r}


```
 

## Level 2: 


```{r}

```
 

## Level 3: 


 
```{r}


```

## Level 4: 


```{r}



```

