---
title: "PsiChi Oct 2021-Jan 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages

```{r}
library(tidyverse)
library(here)
library(janitor)
library(haven)
library(naniar) # vis_miss() 
library(ggpubr) # correlations on scatter plots
library(report)

```

# read data 

```{r}

hookup <- read_sav(here("data", "Hookup Culture Final Data 2.9.21.sav"))
 
```



Our OCTOBER 2021 through JANUARY 2022 contests use Hookup data from Goyette & Spencer (2021).

https://osf.io/v4yhu/ contains information about the study.

https://osf.io/9chb7/ contains an SPSS (.sav) file, that can be imported into R using the "foreign" package. Here are instructions on doing this.



# October 2021

Your tasks for the PsiChiR contest include:

## Level 1 

Remove participants who say they are in a relationship (using variable “RelStatus”, 1 = Single, 2 = in a relationship)

```{r}
#ctrl shift M to get a pipe

hookup %>% 
  tabyl(RelStatus)

## filter == is match and != is non match

hookup_single <- hookup %>%
  filter(RelStatus == 1)

```



## Level 2

Compute Mean and SD for the variable “Age”

```{r}
age_HC <- hookup %>%
  select(ID, Age, HCTotal)

age_HC$Age <- as.numeric(age_HC$Age)


age_HC %>%
  summarise(mean_age = mean(Age, na.rm = TRUE), 
            stdev_age = sd(Age, na.rm = TRUE), 
            min_age = min(Age, na.rm = TRUE), 
            max_age = max(Age, na.rm = TRUE))

age_HC %>%
  tabyl(Age)

```




## Level 3

Create a scatterplot plotting “Age” against “HCTotal”

### JENNY work out why age values disappeared! 

```{r}
age_HC <- age_HC %>%
  na.omit() 

# convert numeric to factor (so that we can get different colours by Age in the plot

age_HC$Age <- as.factor(age_HC$Age)

#check that the factor conversion worked
glimpse(age_HC)


age_HC %>%
  ggplot(aes(x = Age, y = HCTotal, colour = Age)) + 
  geom_point()


```



## Level 4

Correlate “Age” with “HCTotal” (the extent to which participants endorse hookup culture)

```{r}

age_HC$Age <- as.numeric(age_HC$Age)

cor.test(age_HC$Age, age_HC$HCTotal, method= "pearson")

```

```{r message=FALSE, warning=FALSE}

ggscatter(age_HC, x = "Age", y = "HCTotal", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Age", ylab = "Hookup culture identification")
```


# November 2021


Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Remove participants who say they attend religious services

NOTE: the reason in this case we need to tell R that we want it to filter out (!=) the "1" - in quotes, is that R thinks that the AttendService variable is characters. If we converted it to numeric using as.numeric before filtering, we wouldnt need the quotes. 


```{r}

religious <- hookup %>%
  select(ID, Year, Religious, AttendService, HCTotal)

religious %>%
  tabyl(AttendService)


no_religious <- religious %>%
  filter(AttendService != "1")


```


## Level 2
Level 2: Determine frequencies for “Year”

```{r}
count_output <- hookup %>%
  count(hookup$Year)

tabyl_output <- hookup %>%
  tabyl(Year)

# note other option is n() 
```


## Level 3
Level 3: Create a histogram for “HCTotal”

```{r}
hookup %>%
  ggplot(aes(x = HCTotal)) +
  geom_histogram(binwidth = 5)
```



## Level 4

Level 4: Determine whether HCTotal differs across Year

```{r}

HC_summary <- religious %>% 
  group_by(Year) %>% 
  summarise(meanHC = mean(HCTotal, na.rm = TRUE), 
            stdevHC = sd(HCTotal, na.rm = TRUE), 
            n = n(),
            stderrHC = stdevHC/sqrt(n)) 

# changing year to factor (to avoid label related error)

HC_summary$Year <- as.factor(HC_summary$Year)

#checking the factor worked

glimpse(HC_summary)

# plotting year by meanHC w error bars (note: to change the colour of columns, need to use fill rather than colour )

HC_summary %>%
  ggplot(aes(x = Year, y = meanHC, fill = Year)) +
  geom_col() +
  scale_y_continuous(limits = c(0,100), expand = c(0,0)) +
  geom_errorbar(aes(ymin = meanHC-stderrHC, ymax = meanHC + stderrHC),
                  size=.6,    # Thinner lines
                    width=.3) +
  theme_classic()

ggsave("yearplot.png")


# ~ tilde read as by or as a function of 
# save your anova output as an object
# run summary(nameofyourobject) to get F and p values
# run report(nameofyourobject) to get results worthy intepretation/text

hc_year <- aov(HCTotal ~ Year, data = religious)

summary(hc_year)

report(hc_year)

```



# December


Your tasks for the PsiChiR contest include:

## Level 1

Using “Year,” put freshmen and sophomores into one group and juniors/seniors into another group

```{r}

# %in% read as in this list of things

religious2 <- religious %>%
  mutate(group = case_when(Year %in% c(1, 2) ~ "group1", 
                             Year %in% c(3,4) ~ "group2"))
         
         
```


## Level 2

Determine frequencies for this new variable – how many participants are in each new group

```{r}

religious2 %>%
  count(group)

religious2 %>%
  tabyl(group)

religious2 %>%
  group_by(group) %>%
 summarise(n = n())

```


## Level 3

Visually compare these two groups on means for HCTotal

```{r}
# make a descriptive table, M, SD, n, stderr

r2_summary <- religious2 %>%
  group_by(group) %>%
  summarise(meanHC = mean(HCTotal, na.rm = TRUE),
            stdevHC = sd(HCTotal, na.rm = TRUE), 
            n = n(), 
            stderr = stdevHC/sqrt(n))

# plot the mean HC for each group with error bars

r2_summary %>%
  ggplot(aes(x = group, y = meanHC, fill = group)) +
  geom_col() +
  geom_errorbar(aes(ymin = meanHC - stderr, ymax = meanHC + stderr),
                  size=.6,    # Thinner lines
                    width=.3) +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0,80))




```


## Level 4

Statistically compare these two groups on means for HCTotal

```{r}

ttest <- t.test(HCTotal ~ group, data = religious2, paired = FALSE)

report(ttest)

```


# January 2022

## Level 1:

Sort the file by HCTotal scores, from low to high

```{r}

religious2_inc <- religious2 %>%
  arrange(HCTotal, increasing = TRUE)

religious2 %>%
  arrange(desc(HCTotal))

head(religious2_inc)


```


## Level 2:

Compute mean HCTotal scores for each level of “Religion”

```{r}

religious2 %>%
  group_by(Religious) %>%
  summarise(meanHC = mean(HCTotal, na.rm = TRUE))

```


## Level 3:

Create a line graph that shows mean HCTotal scores for two variables: Religion and AttendService

```{r}


plotdata <- religious2 %>%
  group_by(Religious, AttendService) %>%
  summarise(meanHC = mean(HCTotal, na.rm = TRUE),
            stdevHC = sd(HCTotal, na.rm = TRUE), 
            n = n(), 
            stderr = stdevHC/sqrt(n))


plotdata$Religious <- as.factor(plotdata$Religious)

plotdata$AttendService <- as.factor(plotdata$AttendService)

plotdata %>%
  ggplot(aes(x = Religious, y = meanHC, colour = AttendService, group = AttendService)) +
  geom_point(size = 4) +
  geom_line() +
  geom_errorbar(aes(ymin = meanHC - stderr, ymax = meanHC + stderr),
                  size=.6,    # Thinner lines
                    width=.3)


```


## Level 4:

Determine whether there’s an interaction between Religion and AttendService on the variable HCTotal


```{r}

hc_rel_as <- aov(HCTotal ~ Religious + AttendService + Religious:AttendService, data = religious2)

summary(hc_rel_as)

report(hc_rel_as)

# does the shortcut of including just the interaction work to show both main effects and interactoin?
# yes you can tell R that you want both main effect and the interaction without spelling out everything, if you use factor1 * factor2 notation

aov_test1 <- aov(HCTotal ~ Religious:AttendService, data = religious2)

summary(aov_test1)

aov_test2 <- aov(HCTotal ~ Religious*AttendService, data = religious2)


summary(aov_test2)

report(aov_test2)
```

