---
title: "PsiChi Feb-June2022"
output: html_document
date: '2022-05-09'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Our FEBRUARY 2022 through JUNE 2022 contests use data from [Olshan, Vitiello, & Ratliff (2021)](https://cdn.ymaws.com/www.psichi.org/resource/resmgr/journal_2021/26_3_Olshan.pdf)

You can find the data for this study [here](https://osf.io/2qu67/?view_only=dcb2a654248447e6bc2530c0f708093f).

## load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(haven)
library(here)
library(janitor)
library(gt)
library(ggpubr)
library(naniar)
library(ggeasy)
library(report)
```


## read in the data

```{r}

data <- read_sav(here("data", "data_women_OSF_1.25.sav")) %>%
  clean_names()

```




#  FEBRUARY 2022

## Level 1: 
 Write script that will compute the “TotalCog” mean score from the 18 Need for Cognition variables (cog1 through cog18)
 
```{r}

cog <- data %>%
  select(session_id, starts_with("cog"), starts_with("iat"))

# this code is base R

cog_total <- cog %>%
  mutate(cog_mean = rowMeans(x = select(.data = . , starts_with(match = "cog"))))

### ***JENNY work out why rowwise gives bad numbers but the base version above and the longdata-group_by-summarise version below works***

# PROBLEM: this code is tidyverse (but gives values that are rounded to the nearest .5 and DON'T resemble the previous)

cog_total2 <- cog_total %>%
rowwise() %>%
mutate(cog_mean2 = mean(cog1:cog18))

# SOLUTION 1: above code is problematic because of how I am tell R which columns to calculate the mean across
# using c(list of each variable) works better 

cog_total3 <- cog_total2 %>%
  rowwise() %>%
  mutate(cog_mean3 = mean(c(cog1, cog2, cog3_r, cog4_r, cog5_r, cog6, 
                                cog7_r, cog8, cog9_r, cog10, cog11, cog12_r, 
                                cog13, cog14, cog15, cog16_r, cog17, cog18), na.rm = TRUE)) %>%
  ungroup()

# SOLUTION 2: is there a way to use starts_with() to select those variables? ah yes! c_across

cog_total4 <- cog_total3 %>%
  rowwise() %>%
  mutate(cog_mean4 = mean(c_across(cog1:cog18), na.rm = TRUE)) %>%
  ungroup()

# while we are here, that is a lot of decimal places, use round() to reduce to 2dp

cog_total4 <- cog_total3 %>%
  rowwise() %>%
  mutate(cog_mean4 = round(mean(c_across(cog1:cog18), na.rm = TRUE), 2)) %>%
  ungroup()


# ALTERNATIVE: make the wide data into long format using pivot_longer, then use group_by %>% summarise
cog_long <- cog %>%
  pivot_longer(names_to = "item", values_to = "score", cog1:cog18)

# once the data is in long format, we can use group_by and summarise to get a meancog score for each participant

Total_Cog <- cog_long %>%
  group_by(session_id) %>%
  summarise(TotalCog = mean(score))
  
```
 


## Level 2: 
 Create a frequencies table for the TotalCog variable
 
```{r}
Total_Cog %>%
  tabyl(TotalCog)

Total_Cog %>%
  ggplot(aes(x = TotalCog)) +
  geom_histogram(binwidth = 1)

freq <- Total_Cog %>%
  mutate(category = case_when(TotalCog < 3 ~ "cat2",
                              TotalCog > 8 ~ "cat8", 
                              TotalCog >=3 & TotalCog < 4 ~ "cat3", 
                              TotalCog >=4 & TotalCog < 5 ~ "cat4", 
                              TotalCog >=5 & TotalCog < 6 ~ "cat5", 
                              TotalCog >=6 & TotalCog < 7 ~ "cat6", 
                              TotalCog >=7 & TotalCog < 8 ~ "cat7"))

freq %>%
  tabyl(category) %>%
  gt()
```
 

## Level 3: 
 Create a scatterplot of the relation between the cogmean and **IAT scores**
 
```{r my-figure, fig.cap = "Figure 1: The relation between IAT scores and need for cognition scores."}

cog_total %>%
  ggplot(aes(x = cog_mean, y = iat, colour = iat)) +
  geom_point() +
  theme_classic() +
  labs(title = "Figure 1", subtitle = "The relation between IAT scores and need for cognition scores", 
       x = "Need for cognition score", 
       y = "Implicit Association test score", 
       caption = "sample size N = 282") +
  theme(plot.title = element_text(face = "bold")) +
  theme(plot.subtitle = element_text(face = "italic"))

```
 

## Level 4: 
 Run correlation between the TotalCog and IAT scores. Calculate probability value and CIs.
 
```{r}
cor.test(cog_total$cog_mean, cog_total$iat, method= "pearson")

ggscatter(cog_total, x = "cog_mean", y = "iat", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Need for cognition score", ylab = "Implicit Association score")
```



#  MARCH 2022


## Level 1: 
 Exclude participants with missing “STEMTotal” value
 
```{r}

stem <- data %>%
  select(session_id, age, ste_mtotal, starts_with("iat"))

stem %>%
  vis_miss()

stem %>%
  tabyl(ste_mtotal)


stem_nona <- stem %>%
  filter(!is.na(ste_mtotal)) # keep the participants for whom stemtotal is NOT NA (note will delete the whole row if STEMtotal is NA)

stem_nona %>%
  vis_miss()
```
 



## Level 2: 
 Calculate descriptive statistics for the IAT variable
 
 - mean, median
 - max, min
  - stddev, stderr
 
 
kableExtra package useful for table formatting, particularly easy to change digits to however many places you want (avoid need to add round() to every line of your summarise). 
 
 
```{r}
forkable <- stem_nona %>%
  summarise(meanIAT = round(mean(iat), 3),
            medianIAT = round(median(iat), 3),
            maxIAT = round(max(iat), 3),
            minIAT = round(min(iat), 3), 
            stdevIAT = round(sd(iat), 3),
            nIAT = n(), 
            stderrIAT = round(stdevIAT/sqrt(nIAT),3) ) 


kable(forkable, digits = 1) %>%
  kable_styling()



```
 


## Level 3:
 Create a box and dot plot of the IAT variable
 
 
```{r}

stem_nona <- stem_nona %>%
  mutate(x = "x")


# JENNY TO WORK OUT HOW TO MAKE BOX AND JITTER SIT NEXT TO EACH OTHER-- DODGE?

stem_nona %>%
  ggplot(aes(x = x, y = iat)) +
  geom_boxplot(width = 0.5, fill = "pink", alpha = 0.5) +
  geom_jitter(width = 0.1, alpha = 0.5, colour = "#9900CC") +
  theme_classic()
  
```


## Level 4: 
 Calculate a one-sample t-test testing whether the sample's mean IAT score is different from zero
 
```{r}

t.test(iat ~ 1, data = stem_nona)

iat_test <- t.test(stem_nona$iat, mu = 0)

report(iat_test)


```


#  April 2022


## Level 1: 
 Transform age variable into the following groups: 18 to 22; 23 to 30; 31 to 40; 41 to 50; over 50
 
```{r}

stem_nona_age <- stem_nona %>%
  mutate(age_category = case_when(age <=22 ~ "18to22", 
                                  age >=23 & age <= 30 ~ "23to30", 
                                   age >=31 & age <= 40 ~ "31to40", 
                                   age >=41 & age <= 50 ~ "41to50", 
                                  age> 50 ~ "50plus") )

stem_nona_age %>%
  tabyl(age_category)

```
 

## Level 2: 
 Calculate descriptive statistics for the IAT variable separately for each group of the categorical age group you just created
 
## Level 3: ***
 Create a bar graph w/ error bars displaying the IAT scores based on the categorical age variable
 
 https://jennyrichmond.netlify.app/blog/i-dont-have-to-google-series/2023-04-25-error-bars-on-plots/
 
```{r}

 stem_nona_age %>%
  group_by(age_category) %>%
  summarise(meanIAT = mean(iat), 
            sdIAT = sd(iat), 
            n = n(), 
            stderr = sdIAT / sqrt(n)) %>%
  ggplot(aes(x = age_category, y = meanIAT, fill = age_category)) +
  geom_col() +
  geom_errorbar(aes(ymin = meanIAT - stderr, ymax = meanIAT + stderr), 
                size = 0.3, width = 0.5) +
  labs(title = "this is the title", y = "Mean IAT score", 
       x = "Age category", subtitle = "this is the subtitle", 
       caption = "this is the caption") +
  theme_classic() +
  scale_y_continuous(limits = c(0,0.5), expand = c(0,0)) +
  easy_remove_legend()

ggsave("iat_age.png")

```
 

 
## Level 4: ******

Calculate a one-way ANOVA testing the difference in IAT scores based on the age groups

```{r}
age_aov <- aov(iat ~ age_category + gender + age_category*gender, data = stem_nona_age)

summary(age_aov)

report(age_aov)

```


#  MAY 2022

## Level 1: 
 Filter out the participants who are NOT currently in STEM (select Demo2 = 1)
 


## Level 2: 
 Calculate descriptive statistics for the IAT and STEMtotal variables

## Level 3: 
 Create a scatterplot of the relation between the IAT and STEMtotal variables

## Level 4: 
 Run correlation between the IAT and STEMtotal scores. Calculate probability value and CIs.

