---
title: "Psichi Nov2022-Nov2023"
output: html_document
date: "2023-11-14"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Level 1 data processing
Level 2 descriptive statistics
Level 3 data visualisation
Level 4 inferential statistics

Data for this contest is from Psi Chi's Network for International Collaborative Exchange (NICE). 

Specifically, this data is from the first project ever run by NICE - Understanding Family Dynamics in a Cross-Cultural Sample. 


You can find the data for this study [here](https://osf.io/pwe94).

## load packages

The tidyverse is useful for wrangling and data vis. 
here() helps us tell R where stuff is.
janitor is good for data cleaning.
report will automagically write about result for you. 

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(report)
library(papaja)
library(RColorBrewer)
library(ggeasy)
```


## read in the data

Put your cursor in any line of code and press command enter (or Control Enter on windows) to run that line. Or press the green arrow to run the whole chunk. 

%>% is the pipe, it allows you to string together multiple lines of code to do several steps of process in one go

<- is the assignment operator, it says assign whatever is on the right to the new obejct on the left. 

Here we are reading in a csv file, and using clean_names to make all the variable names lower case and with _ in the gaps. 


```{r message=FALSE, warning=FALSE}

data_nov <- read_csv(here("data", "nice_data", "2022_Nov_NICE.csv")) %>%
  clean_names()

```


chr = character strings
dbl = numbers
lgl = TRUE/False


here are a couple of different ways to look at what kinds of data you are dealing with. glimpse() has nicer output than str()

```{r}

# glimpse(data_nov)

# str(data_nov)


```



#  Nov 2022

## Level 1: 

Write script that will select participants who are 18+ years old


Here we are using tabyl (from the janitor package) to count how many participants are in each of the age categories. Tabyl is useful for getting frequencies. 

Then we are filtering to only include participants who are greater than or equal to 18 years of age (NOTE: we only ended up filtering out NA because there weren't any pp younger than 18). And then we are running tabyl on that new dataframe to check that R is going what we want. 

```{r}

data_nov %>% 
  tabyl(age)

data_nov_adults <- data_nov %>%
  filter(age >= 18)


data_nov_adults %>%
  tabyl(age)

```
 


## Level 2: 

Create a variable called “SDQprosocial” that reflects prosocial behavior exhibited by participants. This is probably asking us to calculate mean scores across the 5 prosocial variable. 

SDQ = Strengths and Difficulties Questionnaire
1) emotional symptoms (5 items)
2) conduct problems (5 items)	
3) hyperactivity/inattention (5 items)	
4) peer relationship problems (5 items)	
5) prosocial behaviour (5 items)

Prosocial: 1consid, 4shares, 9pcaring, 17kind, 20helpout)


### notes re filter and select

filter() is for selecting a subset of rows (i.e. participants older than 18)

select() is for selecting a subset of columns (i.e. only those related to sdq)

First, selecting just demographics and sdq variables. 

Then, selecting just demographics and sdq prosocial variables (1, 4, 9, 17, 20)

Then using names() to check that R is doing what we want. 

```{r}

# glimpse(data_nov_adults)


sdq <- data_nov_adults %>% 
  select(age, gender, countryborn, ethnicity, sdq1:sdq25)


prosocial <- sdq %>% 
  select(age, gender, countryborn, ethnicity, sdq1, sdq4, sdq9, sdq17, sdq20)


names(sdq)

```
 

> NOTE IMPORTANT: when you use rowwise() the dataframe you create is "grouped" by row. You need to ungroup() at the end of the chunk to make it so that the dataframe is no longer grouped by row.

Here we are using rowwise() and mutate() to create a new varibale that is the mean of the prosocial varaibles for each participant. We are creating a new variable in our df called SDQprosocial. Remember to ungroup() at the end. 

```{r}

prosocial <- prosocial %>%
  rowwise() %>%
  mutate(SDQprosocial = mean(c(sdq1, sdq4, sdq9, sdq17, sdq20))) %>%
  ungroup

```


After creating the variable, find the mean and standard deviation for prosocial behavior exhibited by participants.

> NOTE IMPORTANT: group_by() groups the data in the output by a grouping variable, it is important to use ungroup() so that when you go to use that dataframe down the line, it isn't still grouped


This chunk demonstrates how to use ungroup() with summarise() to get separate descriptives by gender. Rememebr that group_by also needs a ungroup at the end. Create new df with descriptives for male/female/other separately. 

Then checking the count of male and female participants (frequencies) with tabyl(). Turns out there is only 1 participant in the other category. 

```{r}

# average of all 480 obs

prosocial %>%
  summarise(mean_prosocial = mean(SDQprosocial),
            stdev_prosocial = sd(SDQprosocial), 
            min_prosocial = min(SDQprosocial), 
            max_prosocial = max(SDQprosocial))

# average separate for 1 male 2 female 3 nonbinary

gender_descriptive <- prosocial %>%
  group_by(gender) %>%
  summarise(mean_prosocial = mean(SDQprosocial),
            stdev_prosocial = sd(SDQprosocial), 
            min_prosocial = min(SDQprosocial), 
            max_prosocial = max(SDQprosocial)) %>%
  ungroup()

prosocial %>%
  tabyl(gender)
  
```



## Level 3: 

Create a bar graph to display mean scores on the SDQ variable for men and women.

geom_bar() is best used for frequencies, height of bar is a count
geom_col() is best used for calculated scores, height of your bar is a mean.

 
R cares what kind of data you are working with. It will assume that 1s and 2s are numeric. If you want them to be categorical, you can change that variable to be a factor. Side effect- you can no longer do "number:" things to it. 
 
 %in% is a handy operator for filter- it "reads" as "within this list"
 
NOTE: if you want you bars filled the same, put the put the fill with your geom
for bars, fill = the middle, colour = the outside edge

Here we are first changing the gender variable from numeric to factor and then glimpsing to make sure R has done what we want. 

Then we are plotting gender on the x axis and mean score on the y, as columns. 

Then we are filtering %in% to only get 1 and 2 (male and female) before makign the same plot, but pretty. 

Here we have filled the bars, added a title with labs(), and applied theme_classic(). the scale_y_continuous makes the bars sit on the x axis. 
 
```{r}

gender_descriptive$gender <- as.factor(gender_descriptive$gender)

glimpse(gender_descriptive)

gender_descriptive %>%
  ggplot(aes(x = gender, y = mean_prosocial)) +
  geom_col()


gender_descriptive %>%
  filter(gender %in% c(1, 2)) %>%
  ggplot(aes(x = gender, y = mean_prosocial)) +
  geom_col(width = 0.5, fill = "hotpink", colour = "purple") +
  labs(title = "Mean prosocial scores on SDQ for male and female participants", 
       subtitle = "very small difference", 
       caption = "this is an ugly graph", 
       y = "Mean Prosocial score", x = "Gender") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0)) 

```


Here we are playing with how you could fill you bars by a variable (ie. have different fill for male and female. )

```{r}

# if you want you bars filled BY a variable within your dataset, put the fill with your x and y aesthetics

gender_descriptive %>%
  filter(gender %in% c(1, 2)) %>%
  ggplot(aes(x = gender, y = mean_prosocial, fill = gender)) +
  geom_col(width = 0.5) +
  labs(title = "Mean prosocial scores on SDQ for male and female participants", 
       subtitle = "very small difference", 
       caption = "this is an ugly graph", 
       y = "Mean Prosocial score", x = "Gender") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0))


```

## Level 4: 

Test whether men and women differ on this variable.

We are going to run a t-test. FIrst we need to filter to remove the 1 participant in the other gender category. 

Then we need to make gender a factor. 

glimpse() to check that R did what we want. 

Then we run a t.test using the formula, lookung for differences in DSQ as a function of gender (SDQprosocial ~ gender, data = df)

We are also using report to automagically write about the outcome of our test. 

1= male 
2 = female


```{r}

MFprosocial <- prosocial %>%
  filter(gender %in% c(1,2))


MFprosocial$gender <- as.factor(MFprosocial$gender)

glimpse(MFprosocial)

# X ~ Y formula reads as we interested in X "as a function of Y"
# extra as a function of group
# prosocial as a function of gender

# t.test(extra ~ group, data = sleep) (example from the help)

ttest <- t.test(SDQprosocial ~ gender, data = MFprosocial)

report(ttest)

```


#  Dec 2022

## read in the data

Here I am reading teh dec data in using read-csv and here. Add clean_names to make the variables name all lower case and _ in the gaps. 

```{r message=FALSE, warning=FALSE}

data_dec <- read_csv(here("data", "nice_data", "2022_Dec_NICE.csv")) %>%
  clean_names()

```


## Level 1: 

Write script that will filter out participants who are older than 19

```{r}
data_dec %>%
tabyl(age)

data_dec_adult <- data_dec %>%
  filter(age <= 19)

data_dec_adult %>%
  tabyl(age)

```
 


## Level 2: 

Create a variable called ‘FACEenmesh’ that measures participants’ levels of enmeshment with their families. To create this variable, you will add together the following items from the FACES scale: FACES4, FACES10, FACES16, FACES22, FACES28, FACES34, FACES40

Find the mean and standard deviation for enmeshment exhibited by participants as measured by the FACES

Here i am using the names() function to check the variable names. 

Then I am selecting variables related to demographics and the 7 FACE variables we need. I am creating a new variable using mutate() that adds together the 7 face variabels for each participant. (NOTE: not sure why we don't need rowwise() in this case, but just running with it)

NOTE re NAS
- R does not like calcuate means (or anything else) on variables that contain NAs. When you want to get descriptives and there are NAs in the variable, use na.rm (i.e NA remove) to make R ignore the NAs and calc the mean with the rest of the numbers. The na.rm = TRUE should go WITHIN the bracket with the variable mean(variable, na.rm = TRUE)
 
```{r}

names(data_dec_adult)

faces <- data_dec_adult %>%
  select(age:stateborn, faces4, faces10, faces16, faces22, faces28, faces34, faces40) %>%
  mutate(face_enmesh = faces4 + faces10 + faces16 + faces22 + faces28 + faces34 + faces40)


glimpse(faces)

faces %>%
  summarise(mean_faces = mean(face_enmesh, na.rm = TRUE), 
            sd_faces = sd(face_enmesh, na.rm = TRUE))

```
# re the papaja package
# theme_apa() 

To install the papaja package, type install.packages("papaja") into the console and press enter. 
When it asks you if you want to restart R, say NO
Then to check whether it worked, type library(papaja) to load the package. 


## Level 3: 
Create a bar graph to display mean scores on the enmeshment variable for men and women.

1= male
2= female

 
```{r}

face_gender <- faces %>%
  group_by(gender) %>%
  summarise(mean_faces = mean(face_enmesh, na.rm = TRUE)) %>%
  ungroup() 

glimpse(face_gender)

face_gender$gender <- as.factor(face_gender$gender)

face_gender %>%
  filter(gender %in% c(1, 2)) %>%
  ggplot(aes(x = gender, y = mean_faces, fill = gender)) +
  geom_col(width = 0.6) +
  theme_apa() +
  scale_y_continuous(expand = c(0,0))
```

## Level 4: 

Test whether men and women differ on this variable.
```{r}

faces_MF <- faces %>%
  filter(gender %in% c(1,2))

faces_MF$gender <- as.factor(faces_MF$gender)

glimpse(faces_MF)

gender_test <- t.test(face_enmesh ~ gender, data = faces_MF)

report(gender_test)

```


#  Jan 2023

## read in the data

```{r}

data_jan <- read_csv(here("data", "nice_data", "2023_Jan_NICE.csv")) %>%
  clean_names()

```


## Level 1: 

Write script that will filter out participants who do not have any siblings

```{r}

glimpse(data_jan)

jan <- data_jan %>%
  select(age, gender, countryborn, siblings, faces43:faces52)

glimpse(jan)

jan %>% 
  tabyl(siblings)

jan_siblings  <- jan %>%
  select(age, gender, siblings, faces43:faces52) %>%
  mutate(number_siblings = parse_number(siblings)) %>% 
  mutate(number_siblings_fixed = case_when(siblings == "One" ~ 1, 
                                            siblings == "one biological older sister" ~ 1, 
                                           siblings == "none, only child" ~ 0, 
                                           siblings == "None" ~ 0, 
                                           siblings == "one" ~ 1, 
                                           .default = number_siblings))


jan_no_siblings <- jan_siblings %>%
  filter(number_siblings_fixed >=1)

```

parse_number() will pull the first number from a column

We have 8 failures
- One
- one biological older sister
- none, only child
- None
- one


## AN ASIDE: 

### how to join dataframes using rbind

how to join things

```{r}
dec <- read_csv("data/nice_data/2022_Dec_NICE.csv") %>%
  clean_names() %>%
  select(progress, age, gender, countryborn)

glimpse(dec)

jul <- read_csv("data/nice_data/2023_Jul_NICE.csv") %>%
     clean_names() %>%
     select(progress, age, gender, countryborn)

nov <- read_csv("data/nice_data/2023_Jul_NICE.csv") %>%
     clean_names() %>%
     select(progress, age, gender, countryborn)

glimpse(jul)

dec_jul <- rbind(dec, jul, nov)
  
```



## Level 2: 

Create a variable called ‘FACEcomm’ that measures participants’ levels of communication with their families. 

To create this variable, you will add together the following items from the FACES scale: FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52


Find the mean and standard deviation for communication exhibited by participants as measured by the FACES.

You can avoid writing out all the variables that you want to sum together using this sum(across(v1:v5)), BUT you need to use a rowwise first, not sure why...


```{r}

face_comm <- jan_no_siblings %>%
  rowwise() %>%
  mutate(FACEcomm = sum(across(faces43:faces52))) %>%
  ungroup()
  

```
 

## Level 3: 

 Create a bar graph to display mean scores on the communication variable for men and women.
 
 We wanted to change the colours from the default, so installe RColorBrewer package. You can make all of the available palettes display in your console by typing display.color.brewer() 
 
 Use scale_fill_brewer(palette = "nameofpalette") to change the colour scheme. 
 
 Alterantively you can use scale_fill_manual(values = c("colour1", "colour2")) to pick colours manually. 
```{r}
face_comm_gender <- face_comm %>%
  group_by(gender) %>%
  summarise(mean_comm = mean(FACEcomm, na.rm = TRUE)) %>%
  ungroup()
  
  glimpse(face_comm_gender)

  face_comm_gender$gender <- as.factor( face_comm_gender$gender)
  

  face_comm_gender %>%
    tabyl(gender) 
  
face_comm_gender %>%
    filter(gender %in% c(1,2)) %>%
             ggplot(aes(x = gender, y = mean_comm, fill = gender)) +
  geom_col(width = 0.5) +
  theme_apa() +
  scale_y_continuous(expand = c(0,0), limits = c(0,40)) +
  scale_fill_manual(values = c("lightblue", "pink")) +
  labs(x = "Gender", y = "Mean communication score") +
  easy_remove_legend() +
  scale_x_discrete(labels = c('Male','Female')) +
  easy_all_text_color(color = "black")

# export figure for our thesis

ggsave("meancommbygender.png")


```

## Level 4: 

Test whether communication differs based on the number of siblings someone has.

Make this problem easier by filtering only siblings 1, 2 or 3. 

```{r}

names(face_comm)


face_comm %>%
  tabyl(number_siblings_fixed)


face_comm_analysis <- face_comm %>%
  select(age, gender, siblings = number_siblings_fixed, FACEcomm) %>%
  filter(siblings %in% c(1, 2, 3))

face_comm_analysis %>%
  glimpse()

face_comm_analysis$siblings <- as.factor(face_comm_analysis$siblings)

levels(face_comm_analysis$siblings)

sibling_anova <- aov(FACEcomm ~ siblings, data = face_comm_analysis)

summary(sibling_anova)

report(sibling_anova)

```


## CHECKING IN: 

### What have we learned

- counting things (tabyl)
- filter()
- select()
- names (get variable names)
- rowwise() %>% mutate() to compute a new variable
  - to get mean across variables for each participant
  - to sum across a set of variables for each participant
- group_by() %>% summarise() (to get summary stats separately for each group)
  - how to deal with NAs (na.rm = TRUE)
- importance of ungroup() after you use rowwise or group_by
- changing data types from char to factor (as.factor)
- ggplot
  - geom_col vs geom_bar
  - filling the bars with colour
  - adding titles, axis labels
  - themes (classic vs. apa)
  - changing text colour
  - removing legends
- mutate %>% case_when (to fix odd data entry, parse number)
- joining dataframes that have the same columns (rbind)
- statistics
  - t.test()
  - anova
- writing about stats with report()


#  Feb 2023- skip

> filter out NAs, compute new variable with sum, summarise mean, sd, median, quartiles, plot bar graph, do t.test
- 

## read in the data

```{r}

data_feb <- read_csv(here("data", "nice_data", "2023_Feb_NICE.csv")) %>%
  clean_names()

```

## Level 1: 


Write script that will filter out participants who are missing a value for the Age variable
 

```{r}


```
 


## Level 2: 
Create a variable called ‘FACErigid’ that measures rigidity among families. To create this variable, you will add together the following items from the FACES scale: FACES5 + FACES11 + FACES17 + FACES23 + FACES29 + FACES35 + FACES41
 
Find the mean, standard deviation, median, and lower and upper quartiles for rigidity exhibited by participants as measured by the FACES
 
 
```{r}

```
 

## Level 3: 
Create a bar graph to display mean scores on the rigidity variable for men and women.
 
 
```{r}


```

## Level 4: 

Test if levels of rigidity differ by gender of participant. 

```{r}



```
 
#  March 2023 - skip

> filter by 2 variables, compute new variable with sum, summarise mean, sd, median, range, plot bar graph, do t.test

## read in the data

```{r}

data_mar <- read_csv(here("data", "nice_data", "2023_March_NICE.csv")) %>%
  clean_names()

```
## Level 1: 


Write script that will filter out participants who are missing a value AND who are older than 18for the Age variable
 

```{r}


```
 


## Level 2: 
Create a variable called ‘PsyContF’ that measures Psychological Control exhibited by the respondent’s Father. To create this variable, you will add together the following items from the DYADS scale: DyadF1+ DyadF2+ DyadF3+ DyadF4+ DyadF5+ DyadF6+ DyadF7
 
Find the mean, standard deviation, median, and range for psychological control exhibited by respondent’s fathers as measured by the DYADS
 

 
```{r}

```
 

## Level 3: 

 Create a bar graph to display mean scores of the PsyContF variable reported by men and women.


```{r}


```

## Level 4: 
Test if levels of reported PsyContF differ by gender of participant.
```{r}



```

#  April 2023 **

> filter 2 variables, compute 2 new variables with sum, summarise mean, sd, median, quartiles, plot scatter, do correlation


## read in the data

```{r}

data_apr <- read_csv(here("data", "nice_data", "2023_Apr_NICE.csv")) %>%
  clean_names()

```
## Level 1: 


Write script that will filter out participants who are missing a value for the Age variable
Write a script that will filter out participants who identify as men
 
Note: you can combine filter with AND & or you can specify a combination of filters with a OR operator |


```{r}

data_apr %>%
  tabyl(age)

women_age <- data_apr %>%
  filter(!is.na(age) & gender == 2)
```
 


## Level 2: 

 Create a variable called ‘SDQhyper’ that measures x exhibited by the participant. To create this variable, you will add together the following items from the SDQ scale: SDQ2 + SDQ10 + SDQ15 + SDQ21 + SDQ25
 
Create a variable called ‘SUtotal’ that measures all substance use exhibited by the participant. To create this variable, you will add together the following items from the YRBS scale: YRBS1 + YRBS2 + YRBS3 + YRBS4 + YRBS5 + YRBS6 + YRBS7 + YRBS8 + YRBS9 + YRBS10 + YRBS11 + YRBS12 + YRBS13 + YRBS14 + YRBS15 + YRBS16 + YRBS17
 
Find the mean, standard deviation, median, and range for SDQhyper
 
```{r}

names(sdq_women_age)

sdq_women_age <- women_age %>%
  select(age, gender, starts_with("SDQ"), starts_with("YRB")) %>%
  mutate(SDQhyper = sdq2 + sdq10 + sdq15 + sdq21 + sdq25) %>%
  rowwise() %>%
  mutate(SUtotal = sum(across(yrbs1:yrbs17), na.rm = TRUE)) %>%
  ungroup()

# cheating by just removing the column of NAs
sdq_women_age_noNA <- sdq_women_age %>%
  janitor::remove_empty(which = c("cols"))

# selecting just the variables we need
sdq_hyper_sutotal <- sdq_women_age %>%
  select(age, gender, SDQhyper, SUtotal)


sdq_hyper_sutotal %>%
  summarise(meansdq = mean(SDQhyper, na.rm = TRUE), 
            sd_sdq = sd(SDQhyper, na.rm = TRUE), 
            median = median(SDQhyper, na.rm = TRUE),
            min_sdq = min(SDQhyper, na.rm = TRUE),
            max_sdq = max(SDQhyper, na.rm = TRUE)
            )

```
 



## Level 3: 

Create a graph to display levels of hyperactivity as a function of age


```{r message=FALSE, warning=FALSE}

sdq_hyper_sutotal %>%
  ggplot(aes(x = age, y = SDQhyper)) +
  geom_jitter(width = 0.1)
  

```

## Level 4: 
Test if there is an association between substance use and reported hyperactivity
```{r message=FALSE, warning=FALSE}


sdq_hyper_sutotal %>%
  ggplot(aes(x = SUtotal, y = SDQhyper)) +
  geom_jitter()

correlation <- cor.test(sdq_hyper_sutotal$SUtotal, sdq_hyper_sutotal$SDQhyper,
         alternative = "two.sided",
         method = "pearson",
         exact = NULL, conf.level = 0.95, continuity = FALSE)

report(correlation)
```

To run a correlation that has p values, note the cor() function

cor.test(x, y,
         alternative = c("two.sided", "less", "greater"),
         method = c("pearson", "kendall", "spearman"),
         exact = NULL, conf.level = 0.95, continuity = FALSE, ...)


#  May 2023 up to here 27may


# AN ASIDE: 

## HOW TO MAKE WIDE DATA LONG

## read in the data

```{r}
library(readxl)

lara <- read_xlsx(here("data", "JohnsonMost_dataspreadsheet_LaraEdits.xlsx")) 

lara_pivot <- lara %>%
  select(gender, starts_with("now"), starts_with("day"), starts_with("month"))

# need names_sep(gobbledegook) to tell R how to separate into two col. 
lara_pivot_long <- lara_pivot %>%
  pivot_longer(names_to = c("when", "effort"), values_to = "dv", cols = now25:month100)

```

## take 2: read in data
```{r message=FALSE, warning=FALSE}

jatos <- read_csv(here("data", "jatos_results.csv")) %>%
  select(trial_type, trial_index, time_elapsed, subject, button_pressed, responses, score, timepoint, indifference_point, effort_level) 

jatos_response <- jatos %>%
filter(!is.na(responses))

jatos_button <- jatos %>%
filter(!is.na(button_pressed))

jatos_interesting_data <- jatos %>%
  select(-button_pressed, -responses, -score) %>%
  filter(trial_type != "instructions") %>%
  filter(trial_index >=12)
```

# how to use R to read many datafiles into a single data frame

https://jennyrichmond.netlify.app/blog/use-map-to-read-many-csv-files/

```{r}
files <- dir(pattern = "*.csv")

files

data1 <- files %>%
  map(read_csv) %>% 
  reduce(rbind)
```


# HOW TO recode your group variable

```{r}
data_condition <- honours %>%
  mutate(condition = case_when(
    !is.na(cued_recall_q1) ~ "different",
    !is.na(mc_test_1_q1) ~ "same",
    !is.na(restudy_b1_q_1) ~ "restudy",
    TRUE ~ NA_character_))
```


> filter out NAs, compute new variable with sum, summarise mean, sd, median, quartiles, plot histogram, do regression

## read in the data

```{r}

data_may <- read_csv(here("data", "nice_data", "2023_May_NICE.csv")) %>%
  clean_names()

```
## Level 1: 

Write a script that will filter out participants who are missing a value for the ‘Siblings’ variable.


```{r}


```
 


## Level 2: 
Create a variable called ‘FACEdisen’ that measure family disengagement by adding the following items together: FACES3, FACES9, FACES15, FACES21, FACES27, FACES33, FACES39

Create a variable called ‘FACEenmesh’ that measures family enmeshment by adding the following items:  FACES4, FACES10, FACES16, FACES22, FACES28, FACES34, FACES40

Create a variable called ‘FACEcomm’ that measures family communication by adding together the following items: FACES43, FACES44, FACES45, FACES46, FACES47, FACES48, FACES49, FACES50, FACES51, FACES52

Find the mean, standard deviation, median, and range for ‘FACEdisen’, ‘FACEenmesh’, and ‘FACEcomm’. Report the average number of siblings reported by participants and indicate the range. 
 
```{r}

```
 

## Level 3: 

Create a histogram for “FACEcomm”


```{r}


```

## Level 4: 

Test if there is an association between the number of siblings reported by participants and family disengagement, enmeshment, and communication. 

```{r}



```


#  June 2023

> filter out NAs, recode variable, compute new variable with sum, summarise mean, sd, median, quartiles, plot bar graph, do correlation


## read in the data

```{r}

data_jun <- read_csv(here("data", "nice_data", "2023_Jun_NICE.csv")) %>%
  clean_names()

```
## Level 1: 



• Write script that will filter out participants who are missing a value for the Age variable
• Write a script that will recode text entries in the SexOrient Column to Numbers
o Heterosexual should be 1 
o Non-heterosexual should be 2
 

```{r}


```
 

## Level 2: 

 • Create a variable called ‘FACEcomm’ that measures family communication. To create this variable, you will add together the following items from the FACES scale: FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52
 
• Create a variable called ‘FACEdisen’ that measures family disengagement. To create this variable, you will add together the following items from the FACES scale: FACES3 + FACES9 + FACES15 + FACES21 + FACES27 + FACES33 + FACES39 
 
• Create a variable called ‘SUtotal’ that measures all substance use exhibited by the participant. To create this variable, you will add together the following items from the YRBS scale: YRBS1 + YRBS2 + YRBS3 + YRBS4 + YRBS5 + YRBS6 + YRBS7 + YRBS8 + YRBS9 + YRBS10 + YRBS11 + YRBS12 + YRBS13 + YRBS14 + YRBS15 + YRBS16 + YRBS17
 
• Find the mean, standard deviation, median, and range for FACEcomm, FACEdisen, and SUtotal
 
```{r}

```
 

## Level 3: 
• Create a graph that will show levels of family communication reported by men and women
 
```{r}


```

## Level 4: 
 

• Test if there is an association between substance use and family communication and disengagement
```{r}



```


#  July 2023**

> filter by 1 variable, compute new variable with sum, summarise mean, recode w case_when, make a table of counts, anova?

## read in the data

```{r}

data_jul <- read_csv(here("data", "nice_data", "2023_Jul_NICE.csv")) %>%
  clean_names()

```
## Level 1: 

• Write a script that will filter out participants who don’t have any siblings



```{r}


```
 


## Level 2: 

 • Create a variable called SUmarij by adding YRBS8 + YRBS14
• Find the average number of times participants have used marijuana.
• Transform SUmarij into a binary variable where 0 = never used marijuana, and 1 = has used marijuana 


```{r}

```
 

## Level 3: 

 • Use cross-tabs to make a table that shows the counts of marijuana use (never used/has used) by gender
 

```{r}


```

## Level 4: 
• Test if there is an association between marijuana use and number of siblings someone has

```{r}



```


#  August 2023

> filter out NAs, compute new variables WITH reverse scoring with sum, summarise mean, sd, median, quartiles, plot bar graph, do correlation

## read in the data

```{r}

data_aug <- read_csv(here("data", "nice_data", "2023_Aug_NICE.csv")) %>%
  clean_names()

```
## Level 1: 


• Write a script that will filter out participants who are missing values for the age variable


```{r}


```
 


## Level 2: 

• Create a variable called FACEcomm (Family Communication) by adding together the following items FACES43 + FACES44 + FACES45 + FACES46 + FACES47 + FACES48 + FACES49 + FACES50 + FACES51 + FACES52
o Note the average, standard deviation, and median values for the FACEcommvariable.

• Create a variable called SSBQtotal (Total Safe Sex Behavior) through two steps
o 1. Reverse Score SBQ2 INTO SBQ2R, SBQ7 INTO SBQ7R, SBQ8 INTO SBQ8R, SBQ14 INTO SBQ14R, SBQ16 INTO SBQ16R, SBQ17 INTO SBQ17R, SBQ22 INTO SBQ22R, SBQ24 INTO SBQ24R, SBQ25 INTO SBQ25R
▪ 1 = Always 2 = Most of the time 3 = Sometimes 4 = Never

o 2. Add the following items together: SBQ1 + SBQ2R + SBQ3 + SBQ4 + SBQ5 + SBQ6 + SBQ7R + SBQ8R + SBQ9 + SBQ10 + SBQ11 + SBQ12 + SBQ13 + SBQ14R + SBQ15 + SBQ16R + SBQ17R + SBQ18 + SBQ19 + SBQ20 + SBQ21 + SBQ22R + SBQ23 + SBQ24R + SBQ25R
o Note the average, standard deviation, and median values for the SSBQtotalvariable
 
```{r}

```
 

## Level 3: 

 
• Create a bar graph that shows the mean levels of FACEcomm and SSBQtotal
```{r}


```



## Level 4: 
• Test if there is an association between total safe sex behavior (SSBQtotal) and family communication (FACEcomm).
```{r}



```


#  Sept2023

> filter out NAs, compute new variables with sum, summarise mean, sd, median, quartiles, plot bar graph, do correlation and t.test

## read in the data

```{r}

data_sep <- read_csv(here("data", "nice_data", "2023_Sept_NICE.csv")) %>%
  clean_names()

```
## Level 1: 

• Write a script that will filter out participants who are missing values for the ‘Age’ variable
• Write a script that will filter out participants who are missing values for the ‘Stateborn’ variable



```{r}


```
 


## Level 2: 

 • Create a variable called ‘CFPSCompas’ by summing together the following variables: FPS7, FPS8, FPS9, FPS10
o CFPSCompas is a variable that measures Compassionate Reverence 
• Create a variable called ‘FACEsatis’ by summing together the following variables: FACES53, FACES54, FACES55, FACES56, FACES57, FACES58, FACES59, FACES60, FACES61, FACES62
o FACEsatis is a variable that measures Family Satisfaction


```{r}

```
 

## Level 3: 
• Create a graph that shows the mean levels of Family Satisfaction by gender 

 
```{r}


```

## Level 4: 
• Test if there is an association between Compassionate Reverence and Family Satisfaction. Note any key statistics.
• Test if there are any gender differences in mean levels of Family Satisfaction. Note any key statistics.
```{r}



```




#  Nov 2023

> filter out NAs, compute new variable with sum, summarise mean, sd, median, quartiles, plot bar graph, create correlation matrix

## read in the data

```{r}

data_nov <- read_csv(here("data", "nice_data", "2023_Nov_NICE.csv")) %>%
  clean_names()

```
## Level 1: 


·   	Write a script that will filter out participants who are missing values for the ‘Hoursmom’ and ‘Hoursdad’ variables
·   	Create a variable called ‘PsyContM’ by summing together the following variables: DyadM1+ DyadM2+ DyadM3+ DyadM4+ DyadM5+ DyadM6+ DyadM7
·   	Create a variable called ‘PsyContF’ by summing together the following variables:  DyadF1+ DyadF2+ DyadF3+ DyadF4+ DyadF5+ DyadF6+ DyadF7



```{r}


```
 


## Level 2: 

 ·   	Calculate the mean, standard deviation, median, and range for PsyContM and PsyContF
```{r}

```
 

## Level 3: 

Create a correlation matrix for Hoursmom, Hoursdad, PsyContM and PsyContM
 
```{r}


```

## Level 4: 
·   	Is there a significant correlation between PsyConF and Hoursdad? Note the R and P values.
```{r}



```


#  Dec 2023 **

> get descriptives, correlation, recoding, anova


## read in the data

```{r}

data_dec <- read_csv(here("data",  "Flight Data December 2023 Contest.csv")) %>%
  clean_names()

```

## Level 1: 

Provide descriptive statistics for the actual_flown_miles variable. Indicate the minimum number of miles flow, the maximum number of miles flow, the average number of miles flown, and the median number of miles flown.
```{r}


```
 


## Level 2: 

Describe the relationship between satisfaction (satisfaction_score) and delay time (arrival_delay_minutes). Note that for satisfaction_score a value of 1 is the lowest (dissatisfied) and 5 is the highest (satisfied). 

Note that negative values in the arrival delay minutes mean the flight was early, while positive values indicate the flight was late. 
```{r}

```
 

## Level 3: 

Does satisfaction level (satisfaction_score) vary by the cabin (cabin_code) that they’re in? 
 
```{r}


```


## Level 4: 

Describe the relationship between loyalty program membership (loyalty_program_level) and satisfaction (satisfaction_score). Hint: you’ll have to do some recoding for folks who don’t belong to a program

```{r}



```


