---
title: "PsiChi Sept - Dec 2020"
author: "Jen Richmond"
date: '2022-12-26'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r}
library(tidyverse)
library(here)
library(janitor)
```

# read data 

```{r}
data <- read_csv(here("data", "NICE CROWD DATA.csv"))
```


# Sept 2020 

Our September 2020 contest uses data from Psi Chi's NICE:CROWD project.


Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Remove cases that have missing values on "Countryborn"

## Level 2

Level 2: Find frequencies for the following variables: UserLanguage, Gender, and Race

## Level 3
Level 3: Create a scatterplot to visualize the relationship between vertical collectivism (COSvcollect) and horizontal collectivism (COShcollect)

## Level 4

Level 4: Calculate Pearson's R correlation coefficient between vertical collectivism and horizontal collectivism. 

# Oct 2020

Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Create a new variable "Duration in minutes" by taking the variable "Duration__in_seconds_" and dividing it by 60.

## Level 2

Level 2: Find the median for this new variable.

## Level 3

Level 3: Create a bar graph to display medians for men and women.

## Level 4

Level 4: Test whether men and women differ on this variable.



# Nov 2020

Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Recode the FACES satisfaction subscale ("FACEsatis") into three categories: Low (10 - 23), Medium (24 - 37), and High (38 - 50)

## Level 2

Level 2: Calculate the means and standard deviations for the following variables: SSBQTotal, FACEchaotic, and SDQprosocial.

## Level 3
Level 3: Create a bar graph to compare the SSBQTotal means across FACEsatis groups. Include 95% confidence interval error bars

## Level 4
Level 4: Test the hypothesis that SSBQTotal scores differ across the three FACEsatis groups.

# Dec 2020

Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Subset and filter your data so you have a dataset that excludes participants with missing values for "Race" and "Gender", and includes only these two variables plus the variable "COShcollect" (horrizontal collectivism)

## Level 2
Level 2: Calculate the means and standard deviations for COShcollect for all gender categories.

## Level 3
Level 3: Create a line graph that displays mean COShcollect scores for different race categories, with separate lines for each gender.

## Level 4

Level 4: Conduct a factorial ANOVA to compare COShcollect scores across race and gender.