---
title: "PsiChi 2021_Jul-Sept"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# load packages
```{r}
library(tidyverse)
library(here)
library(janitor)
```

# read data 

```{r}
data <- read_csv(here("data", "singleUS.csv"))
```


Our July-Sept 2021 contest uses data from the Singles in America study.

https://osf.io/grujm/ contains a .csv for the data.

https://osf.io/ugb52/ contains a codebook.

# DESCRIPTION OF DATA

Single in America is an annual study on the attitudes and behaviors of single people in America. The study is sponsored by the online dating company Match and is in collaboration with Dr. Helen Fisher and Dr. Justin Garcia at the Kinsey Institute. Every year they ask 5,000 singles about all kinds of things, like what they are looking for in a partner, their dating preferences, their past relationships, and their interests.

The researchers used a stratified random sampling technique to select the participants from a list of people who signed up to be considered in research opportunities. This means that the researchers purposefully selected particular demographic categories, or strata. Then they randomly selected individuals within each of the categories, proportionate to their assumed membership in the population. The proportions they used were based on the most recent US Census.

All participants completed the survey over the internet. Participants were required to authenticate their identity before starting the survey. If there was evidence that participants used a response set to answer the questions (like if they answered the first option for every question) or if the survey was completed too quickly, their data was not included in the study.

We will use a randomly selected subset of the 2016 singles in America dataset several times throughout this guide. Note that this data is a subsample of a real dataset collected through the Kinsey Institute and match.com.

# JULY CHALLENGE

In the Singles in America study, the participants were asked a series of questions about judging others based on different things, like their social media pictures.

Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Create the total superficial judgment summary score (i.e., sum judge_pic, judge_outfit, judge_job, judge_born, judge_live, judge_car, judge_uni, judge_diet, judge_drink, judge_teeth, judge_posts, judge_grammar, judge_sparetime)

## Level 2

Level 2: Examine the total superficial judgment summary score with a histogram.

## Level 3

Level 3: Compute mean/median/mode/standard deviation for the total superficial judgment summary score.

## Level 4

Level 4: Compute means and standard deviation for superficial judgment summary by "onenight" group & do a t-test.



# AUGUST CHALLENGE

In the Singles in America study, the participants were asked a series of questions about judging others based on different things, like their social media pictures.

Your tasks for the PsiChiR contest include:

## Level 1

Create a total white lies summary score (i.e., sum whitelie_age, whitelie_divorce, whitelie_kids, whitelie_live, whitelie_job, whitelie_finance, whitelie_interest, whitelie_sexhistory, whitelie_datehistory).

## Level 2

Examine the total white lies score with a histogram.

## Level 3

Compute mean/median/mode/standard deviation for the total white lies summary score.

## Level 4

Compute means and standard deviation by group & do a t-test



# SEPTEMBER CHALLENGE

In the Singles in America study, the participants were asked a series of questions about judging others based on different things, like their social media pictures.

Your tasks for the PsiChiR contest include:

## Level 1

Create two frequency tables - one for the one night stand variable (onenight) and one for the friends w/ benefits variable (friendwb).


## Level 2
Create a grouped bar plot of the frequencies of the one night stand and friends w/ benefits variables (hint: you can use fill in the aesthetic a ggplot)

## Level 3

Create a frequency table with one night stand in columns and friends w/ benefits in rows

## Level 4

Calculate a chi square test of independence between the friends with benefits & one night stand variable.