---
title: "PsiChi Oct-Jan 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r}
library(tidyverse)
library(here)
library(janitor)
library(haven)
```

# read data 

```{r}
data <- read_sav(here("data", "data_women_OSF_1.25.sav"))
```


Our OCTOBER 2021 through JANUARY 2022 contests use Hookup data from Goyette & Spencer (2021).

https://osf.io/v4yhu/ contains information about the study.

https://osf.io/9chb7/ contains an SPSS (.sav) file, that can be imported into R using the "foreign" package. Here are instructions on doing this.



# October 2021

Your tasks for the PsiChiR contest include:

## Level 1 

Remove participants who say they are in a relationship (using variable “RelStatus”, 1 = Single, 2 = in a relationship)


## Level 2

Compute Mean and SD for the variable “Age”



## Level 3

Create a scatterplot plotting “Age” against “HCTotal”




## Level 4

Correlate “Age” with “HCTotal” (the extent to which participants endorse hookup culture)




# November 2021


Your tasks for the PsiChiR contest include:

## Level 1

Level 1: Remove participants who say they attend religious services

## Level 2
Level 2: Determine frequencies for “Year”

## Level 3
Level 3: Create a histogram for “HCTotal”


## Level 4

Level 4: Determine whether HCTotal differs across Year


# December


Your tasks for the PsiChiR contest include:

## Level 1

Using “Year,” put freshmen and sophomores into one group and juniors/seniors into another group

## Level 2

Determine frequencies for this new variable – how many participants are in each new group

## Level 3

Visually compare these two groups on means for HCTotal

## Level 4

Statistically compare these two groups on means for HCTotal